---
title: "Does item format impact response?"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
---

The primary aims of this study are to evaluate the effects of item wording in online, self-report personality assessment. Specifically, we intend to consider the extent to which incremental wording changes may influence differences in the distributions of responses, response times, and psychometric properties of the items. These wording changes will include a progression from using (1) trait-descriptive adjectives by themselves, (2) with the linking verb “to be” (Am…), (3) with the additional verb “to tend” (Tend to be...), and (4) with the pronoun “someone” (Am someone who tends to be…). 

Using a protocol that administers each adjective twice to the same participant (in different combinations of item format administered randomly across participants), we will use between-person analyses to compare responses using group-level data for the different formats. 

These analyses will attempt to account for delayed_memory effects by collecting data on immediate and delayed recall (5 minutes and approximately two weeks) using a delayed_memory paradigm that was developed based on a similar recall task used in the HRS (Runge et al., 2015).


```{r analysisFormat1, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

```{r analysisFormat2, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(lme4) # for mulitlevel modeling
library(lmerTest) # for p-values
library(emmeans) # for comparisons
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
library(broom.mixed) # for tidying mulitievel models
library(papaja) # pretty numbers
```

```{r analysisFormat3, echo = F}
load(here("objects/items_df.Rds"))
load(here("objects/bfmm_df.Rds"))
load(here("objects/reverse_vector.Rds"))
```

## Effect of format on response (Block 1 and 2)

We used a multilevel model, nesting response within participant to account for dependence. Our primary predictor was format. Here, we use data from Blocks 1 and 2. As a reminder, each participant was presented with only one of the four formats during Block 1 and all four formats during Block 2. Thus, each participant's response style to one of the formats is well characterized, although each participant contributes data to all four styles, and thus we have a within-person design. We use the `anova` function to estimate the amount of variability in response due to format.

```{r analysisFormat13}
items_12 = items_df %>% filter(block %in% c("1","2"))
```

We also remove the Big Five Mini Markers.

```{r}
items_12 = items12 %>% select(-any_of(bfmm))
```


```{r analysisFormat14}
mod.format_b2 = lmer(response~format + (1|proid) + (1|block),
                  data = items_12)
anova(mod.format_b2)
```


```{r analysisFormat14b, echo = F}
fb2_aov = anova(mod.format_b2)
fb2_sig = fb2_aov$`Pr(>F)`[[1]] < .05
fb2_aov = fb2_aov %>% 
  as_tibble() %>% 
  rename(Fval = `F value`,
         Pval = `Pr(>F)`) %>% 
  mutate(across(starts_with("P"), printp),
         across(where(is.numeric), printnum))
```

When examining both Block 1 and Block 2 data, item format was `r ifelse(fb2_sig, "associated", "unassociated")` with participants’ responses to personality items $(F(`r fb2_aov$NumDF[[1]]`, `r fb2_aov$DenDF[[1]]`) = `r fb2_aov$Fval[[1]]`, p = `r fb2_aov$Pval[[1]]`)$. You can see the effect visualized in Figure \@ref(fig:analysisFormat16). In addition, the full histogram of responses to each format are presented in Figure \@ref(fig:analysisFormat17).

```{r analysisFormat15, echo = F}
# save for power analysis
save(mod.format_b2, file = here("objects/mod_format_b2.Rdata"))
```


```{r analysisFormat16, fig.cap = "Predicted response on personality items by condition, using Block 1 and Block 2.", echo =F}
plot_b2 = plot_model(mod.format_b2, type = "pred")

plot_b2$format +
  labs(x = NULL,
       y = "Average response",
       title = NULL) +
  theme_pubclean()
```

```{r analysisFormat17, echo = F, fig.cap = "Distribution of responses by category, block 1 and block 2"}
means_by_group = items_12 %>%
  group_by(format) %>%
  summarise(m = mean(response),
            s = sd(response))

items_12 %>%
  ggplot(aes(x = response, fill = format)) +
  geom_histogram(bins = 6, color = "white") +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  geom_text(aes(x = 1,
                y = 200,
                label = paste("M =", round(m,2),
                              "\nSD =", round(s,2))),
            data = means_by_group,
            hjust =0,
            vjust = 1) +
  facet_wrap(~format) +
  guides(fill = "none") +
  scale_x_continuous(breaks = 1:6) +
  labs(y = "Number of particpants",
       title = "Distribution of responses by format (Block 1 and Block 2)") +
  theme_pubr()
```

### One model for each adjective

We can also repeat this analysis separately for each trait. We use the `anova` function to estimate the variability due to format and print the corresponding _F_-test.

```{r analysisFormat18, results = 'asis'}
mod_by_item_b2 = items_12 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lmer(response~format + (1|proid), data = .))) %>%
  mutate(aov = map(mod, anova))
```

To present these results, we use the `tidy` function to summarize the findings and extract just the _F_-test associated with the format variable. We calculate adjusted _p_-values using a Holm correction. We also create a column that indicates whether the item was reverse-scored; we use this to sort the table, in case a pattern emerges. See the final version of this in Table \@ref(tab:analysisFormat19).

```{r analysisFormat19, echo = F}
summary_by_item_b2 = mod_by_item_b2 %>%
  ungroup() %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>%
  unnest(cols = c(tidy)) %>%
  filter(term == "format") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>%
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_b2 %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>%
  select(item, reverse, sumsq, meansq, NumDF, DenDF, statistic, p.value, p.adj) %>%
  kable(digits = 2,
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df1", "df2", "F", "raw", "adj"),
        booktabs = T, caption = "Format effects on response by item (block 1 data only)") %>%
  kable_styling() %>%
    add_header_above(c(" " = 7, "p-value" = 2))
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r analysisFormat20}
sig_item_b2 = summary_by_item_b2 %>%
  filter(p.value < .05)

sig_item_b2 = sig_item_b2$item
sig_item_b2
```

Then we create models for each adjective. We use the `emmeans` package to perform pairwise comparisons, again with a Holm correction on the _p_-values. We also plot the means and 95% confidence intervals of each mean.

**This code will have to be changed after final data collection. It is not self-adapting!**

### Careless

The pairwise comparisons of responses to different forms of "careless" are displayed in Table \@ref(tab:analysisFormat21) and Figure \@ref(fig:analysisFormat22).

```{r analysisFormat21, echo = F, results = 'asis'}
careless_model_b2 = items_12 %>%
  filter(item == "careless") %>%
  lmer(response~format + (1|proid),
                               data = .)

careless_em_b2 = emmeans(careless_model_b2, "format")
pairs(careless_em_b2, adjust = "holm") %>%
  as_tibble() %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in response to Careless by format (Block 1 and Block 2)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r analysisFormat22, echo = F, fig.cap = "Average response to \"careless\" by format (Block 1 and Block 2)" }
plot_model(careless_model_b2, type = "pred", terms = c("format"))
```


### Thrifty

The pairwise comparisons of responses to different forms of "thrifty" are displayed in Table \@ref(tab:analysisFormat23) and Figure \@ref(fig:analysisFormat24).


```{r analysisFormat23, results = 'asis', echo = F}
thrifty_model_b2 = items_12 %>%
  filter(item == "thrifty") %>%
  lmer(response~format + (1|proid),
                               data = .)

thrifty_em_b2 = emmeans(thrifty_model_b2, "format")
pairs(thrifty_em_b2, adjust = "holm") %>%
  as_tibble() %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in response to Thifty by format (Block 1 and Block 2)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r analysisFormat24, fig.cap = "Average response to \"thrifty\" by format (Block 1 and Block 2)", echo = F}
plot_model(thrifty_model_b2, type = "pred", terms = c("format"))
```

## Account for memory effects (Blocks 1 and 2)

One limitation of the two-blocks model is that format effects may depend on a person's memory. For example, suppose that participants, in general, are more likely to respond with a 6 to items containing "tend to" (e.g., "tend to be outgoing") than to items that only start with "am" (e.g., "am outgoing"). However, if a participant remembers that on the first presentation of the item they selected 4, they may be more likely choose 4 again to appear consistent. This example posits that memory moderates format's effect on response. We model this possibility using participant's delayed memory scores, or their recall score 10 minutes after seeing the list of words.

```{r analysisFormat25}
mod.format_mem = lmer(response~format*delayed_memory + (1|proid),
                  data = items_12)
anova(mod.format_mem)
```


```{r analysisFormat25b, echo = F}
fmem_aov = anova(mod.format_mem)
fmem_sig1 = fmem_aov$`Pr(>F)`[[2]] < .05
fmem_sig2 = fmem_aov$`Pr(>F)`[[3]] < .05
fmem_aov = fmem_aov %>% 
  as_tibble() %>% 
  rename(Fval = `F value`,
         Pval = `Pr(>F)`) %>% 
  mutate(across(starts_with("P"), printp),
         across(where(is.numeric), printnum))
```

When examining both Block 1 and Block 2 data, memory `r ifelse(fmem_sig1, "had", "did not have")` a main effect on participant responses $(F(`r fmem_aov$NumDF[[2]]`, `r fmem_aov$DenDF[[2]]`) = `r fmem_aov$Fval[[2]]`, p = `r fmem_aov$Pval[[2]]`)$ and `r ifelse(fmem_sig2, "did", "did not")` moderate differences between formats $(F(`r fmem_aov$NumDF[[3]]`, `r fmem_aov$DenDF[[3]]`) = `r fmem_aov$Fval[[3]]`, p = `r fmem_aov$Pval[[3]]`)$. See these results in Figure \@ref(fig:analysisFormat26). 


```{r analysisFormat26, fig.cap = "Predicted response on personality items by condition after controlling for memory (10 minute).", echo = F}
plot_model(mod.format_mem,
           type = "pred",
           term = c("format", "delayed_memory[meansd]")) +
  geom_line() +
  labs(x = NULL,
       y = "Average response") +
  scale_color_discrete("Memory", labels = c("-1SD", "Mean", "+1SD"))+
  theme_pubclean()
```

### One model for each adjective

Again, we test this model within each trait adjective, to determine whether the moderating effect of memory is stronger for any particular trait(s). The results are summarized in Table \@ref(tab:analysisformat27).

```{r analysisformat27, results = 'asis', echo = F}
mod_by_item_mem = items_12 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lm(response~format*delayed_memory, data = .))) %>%
  mutate(aov = map(mod, anova))

summary_by_item_mem = mod_by_item_mem %>%
  ungroup() %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>%
  unnest(cols = c(tidy)) %>%
  filter(term == "format:delayed_memory") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>%
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_mem %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>%
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>%
  kable(digits = 2,
         col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df", "F", "raw", "adj"),
        caption = "Test of interaction of format and memory for individual adjectives",
        booktabs = T) %>%
  kable_styling() %>%
  add_header_above(c(" " = 6, "p-value" = 2))
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r analysisFormat28}
sig_item_mem = summary_by_item_mem %>%
  filter(p.value < .05)

sig_item_mem = sig_item_mem$item
sig_item_mem
```

## Inclusion of "I" (Block 1 and Block 3)

Finally, we test whether the inclusion of the word "I" impacts item response (e.g. "I am outgoing"). We used two multilevel models, nesting response within participant to account for dependence. Our primary predictors are format and also the presence of the word "I". Because we have no specific rationale for how or why "I" would impact responses, we test both the partialled main effect of "I" as well as the interaction with format. Here, we use data from Blocks 1 and 3. Results are presented in Figure \@ref(fig:analysisFormat32) and the full distribution of responses by format and "i" are presented in Figure \@ref(fig:analysisFormat33).

```{r analysisFormat29}
items_13 = items_df %>%
  filter(block %in% c("1","3")) %>%
  filter(condition != "A") %>%
  filter(time2 == "yes")
```

```{r analysisFormat30}
mod.format_b3_1 = lmer(response~format + i + (1|proid),
                  data = items_13)
anova(mod.format_b3_1)

mod.format_b3_2 = lmer(response~format*i + (1|proid),
                  data = items_13)
anova(mod.format_b3_2)
```

```{r analysisFormat31, echo = F}
# save for power analysis
save(mod.format_b3_2, file = here("objects/mod_format_b3.Rdata"))
```


```{r analysisFormat32, fig.cap = "Predicted response on personality items by condition, using only Block 1 data.", echo = F}
plot_b3 = plot_model(mod.format_b3_2, type = "pred", terms = c("format", "i"))
plot_b3 +
  geom_line() +
  labs(x = NULL,
       y = "Average response",
       title = "Average responses by item formatting (Block 1 and Block 2)") +
  theme_pubclean()
```

```{r analysisFormat33, echo = F, fig.cap = "Distribution of responses by category, block 1 and block 2"}
means_by_group = items_13 %>%
  group_by(format, i) %>%
  summarise(m = mean(response),
            s = sd(response))

items_13 %>%
  ggplot(aes(x = response, fill = i)) +
  geom_histogram(bins = 6, color = "white") +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  geom_text(aes(x = 1,
                y = 100,
                label = paste("M =", round(m,2),
                              "\nSD =", round(s,2))),
            data = means_by_group,
            hjust =0,
            vjust = 1) +
  facet_grid(i~format, scales = "free") +
  guides(fill = "none") +
  scale_x_continuous(breaks = 1:6) +
  labs(y = "Number of particpants",
       title = "Distribution of responses by format and I (Block 1 and Block 2)") +
  theme_pubr()
```

### One model for each adjective

As before, we test both the additive (Table \@ref(tab:analysisformat34b)) and interaction (Table \@ref(tab:analysisformat35b)) terms of `format` and `i` for each item. 

```{r analysisFormat34, results = 'asis'}
mod_by_item_i = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lmer(response~format + i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, anova))
```
```{r analysisformat34b, results = 'asis', echo = F}
summary_by_item_i = mod_by_item_i %>%
  ungroup() %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>%
  unnest(cols = c(tidy)) %>%
  filter(term == "i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>%
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_i %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>%
  select(item, reverse, sumsq, meansq, NumDF, DenDF, statistic, p.value, p.adj) %>%
  kable(digits = 2,
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df1", "df2", "F", "raw", "adj"),
        booktabs = T, caption = "Effect of \"I\" (block 1 and 3 data)") %>%
  kable_styling() %>%
    add_header_above(c(" " = 7, "p-value" = 2))
```


```{r analysisFormat35, results = 'asis'}
mod_by_item_i2 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lmer(response~format*i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, anova))
```
```{r analysisformat35b, results = 'asis', echo = F}
summary_by_item_i2 = mod_by_item_i2 %>%
  ungroup() %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>%
  unnest(cols = c(tidy)) %>%
  filter(term == "format:i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>%
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_i2 %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>%
  select(item, reverse, sumsq, meansq, NumDF, DenDF, statistic, p.value, p.adj) %>%
  kable(digits = 2,
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df1", "df2", "F", "raw", "adj"),
        booktabs = T, caption = "Interaction of format and \"I\" (block 1 and 3 data)") %>%
  kable_styling() %>%
    add_header_above(c(" " = 7, "p-value" = 2))
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r analysisFormat36}
sig_item_i = summary_by_item_i %>%
  filter(p.value < .05)

sig_item_i = sig_item_i$item
sig_item_i
```

### Curious

The pairwise comparisons of responses to different forms of "curious" are displayed in Table \@ref(tab:analysisFormat37b) and Figure \@ref(fig:analysisFormat38).

```{r analysisFormat37, results = 'asis'}
curious_model_i = items_13 %>%
  filter(item == "curious") %>%
  lmer(response~format*i + (1|proid),
                               data = .)
```
```{r analysisFormat37b, results = 'asis', echo = F}
curious_model_i %>%
  tidy() %>%
  mutate(term = str_replace(term, "\n", " "),
         term = str_replace(term, "format", ""),
         term = str_replace(term, "iPresent", "I")) %>%
  filter(is.na(group)) %>%
  select(-effect, -group) %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Interaction of format and \"I\"",
        col.names = c("Term", "Estimate", "SE",  "t", "df", "p")) %>%
  kable_styling()
```

```{r analysisFormat38, echo = F, fig.cap = "Effect of format and I on responses to the adjective curious"}
plot_model(curious_model_i, type = "pred",
           terms = c("format", "i")) +
  geom_line()
```

### Lively

The pairwise comparisons of responses to different forms of "lively" are displayed in Table \@ref(tab:analysisFormat39b) and Figure \@ref(fig:analysisFormat40).


```{r analysisFormat39, results = 'asis'}
lively_model_i = items_13 %>%
  filter(item == "lively") %>%
  lmer(response~format*i + (1|proid),
                               data = .)
```

```{r analysisFormat39b, results = 'asis', echo = F}
lively_model_i %>%
  tidy() %>%
  mutate(term = str_replace(term, "\n", " "),
         term = str_replace(term, "format", ""),
         term = str_replace(term, "iPresent", "I")) %>%
  filter(is.na(group)) %>%
  select(-effect, -group) %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Interaction of format and \"I\"",
        col.names = c("Term", "Estimate", "SE",  "t", "df", "p")) %>%
  kable_styling()
```

```{r analysisFormat40, echo = F, fig.cap = "Effect of format and I on responses to the adjective lively"}
plot_model(lively_model_i, type = "pred",
           terms = c("format", "i")) +
  geom_line()
```

### Responsible

The pairwise comparisons of responses to different forms of "responsible" are displayed in Table \@ref(tab:analysisFormat41b) and Figure \@ref(fig:analysisFormat42).


```{r analysisFormat41, results = 'asis'}
responsible_model_i = items_13 %>%
  filter(item == "responsible") %>%
  lmer(response~format*i + (1|proid),
                               data = .)
```

```{r analysisFormat41b, results = 'asis', echo = F}
responsible_model_i %>%
  tidy() %>%
  mutate(term = str_replace(term, "\n", " "),
         term = str_replace(term, "format", ""),
         term = str_replace(term, "iPresent", "I")) %>%
  filter(is.na(group)) %>%
  select(-effect, -group) %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Interaction of format and \"I\"",
        col.names = c("Term", "Estimate", "SE",  "t", "df", "p")) %>%
  kable_styling()
```

```{r analysisFormat42, echo = F, fig.cap = "Effect of format and I on responses to the adjective responsible"}
plot_model(responsible_model_i, type = "pred",
           terms = c("format", "i")) +
  geom_line()
```

### Sympathetic

The pairwise comparisons of responses to different forms of "sympathetic" are displayed in Table \@ref(tab:analysisFormat43b) and Figure \@ref(fig:analysisFormat44).


```{r analysisFormat43, results = 'asis'}
sympathetic_model_i = items_13 %>%
  filter(item == "sympathetic") %>%
  lmer(response~format*i + (1|proid),
                               data = .)
```
```{r analysisFormat43b, results = 'asis', echo = F}

sympathetic_model_i %>%
  tidy() %>%
  mutate(term = str_replace(term, "\n", " "),
         term = str_replace(term, "format", ""),
         term = str_replace(term, "iPresent", "I")) %>%
  filter(is.na(group)) %>%
  select(-effect, -group) %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Interaction of format and \"I\"",
        col.names = c("Term", "Estimate", "SE",  "t", "df", "p")) %>%
  kable_styling()
```

```{r analysisFormat44, echo = F, fig.cap = "Effect of format and I on responses to the adjective sympathetic"}
plot_model(sympathetic_model_i, type = "pred",
           terms = c("format", "i")) +
  geom_line()
```

