---
title: "Format effects"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

Within-person analyses will model the proportions of variance attributable to item format, stems of the items (i.e., the content of the adjectives), and the respondent-level variance.

```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

## Workspace

```{r}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(lme4) # for mulitlevel modeling
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
```

```{r, echo = F}
load(here("data/cleaned_data.Rds"))
```


## Data prep

First we select the responses to the items of different formats. These variable names all have the same format: `[trait]_[abcd]` (for example, `talkative_a`). We search for these items using regular expressions.

```{r}
personality_items = str_subset(
  names(data),
  "^([[:alpha:]])+_[abcd]_?2?$"
)

item_responses = data %>%
  select(proid, all_of(personality_items), memory) 
```

Next we reshape these data into long form.

```{r}
item_responses = item_responses %>%
  gather(item, response, -proid, -memory) %>%
  mutate(
    time = ifelse(str_detect(item, "_2"), "2", "1"),
    item = str_remove(item, "_2")) %>%
  separate(item, into = c("item", "format")) %>%
  filter(!is.na(response))
```

## Model

We estimate variance attributable to particpant (`proid`), adjective (`item`), and format (`format`) using a nested model.

```{r}
mod_within_full = lmer(response ~ 1 
                  + (1 | item)
                  + (1 | format)
                  + (1 |proid),
                  data = item_responses)
summary(mod_within_full)

```

```{r}
variances = VarCorr(mod_within_full, comp="Variance")
var_proid  = variances$proid[[1]]
var_item   = variances$item[[1]]
var_format = variances$format[[1]]
var_resid = attr(variances, "sc")^2
var_total = var_proid + var_item + var_format + var_resid
```

Participants account for `r round(100*var_proid/var_total, 2)` percent of the variability in response.

Items account for `r round(100*var_item/var_total, 2)` percent of the variability in response.

Format accounts for `r round(100*var_format/var_total, 2)` percent of the variability in response.

In total, `r round(100*(var_proid+var_item+var_format)/var_total, 2)` percent of the variability in response is explained.

## Significance tests

To test whether each of these factors accounts for a significant amount of variance, we create a model without nesting and test the difference in fits using log likelihood.

```{r}
mod_within_item = lmer(response ~ 1 
                  + (1 | item)
                  + (1 | format)
                  + (1 | proid),
                  data = item_responses)
```

