---
title: "Format effects"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

Within-person analyses will model the proportions of variance attributable to item format, stems of the items (i.e., the content of the adjectives), and the respondent-level variance.

```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

## Workspace

```{r}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(lme4) # for mulitlevel modeling
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
```

```{r, echo = F}
load(here("data/cleaned_data.Rds"))
```


## Data prep

First we select the responses to the items of different formats. These variable names all have the same format: `[trait]_[abcd]` (for example, `talkative_a`). We search for these items using regular expressions.

```{r}
personality_items = str_subset(
  names(data),
  "^([[:alpha:]])+_[abcd]_?2?$"
)

item_responses = data %>%
  select(proid, all_of(personality_items), memory) 
```

Next we reshape these data into long form.

```{r}
item_responses = item_responses %>%
  gather(item, response, -proid, -memory) %>%
  mutate(
    time = ifelse(str_detect(item, "_2"), "2", "1"),
    item = str_remove(item, "_2")) %>%
  separate(item, into = c("item", "format")) %>%
  filter(!is.na(response))
```

## Model

We estimate variance attributable to particpant (`proid`), adjective (`item`), and format (`format`) using a nested model.

```{r}
mod_within_full = lmer(response ~ 1 
                  + (1 | item)
                  + (1 | format)
                  + (1 |proid),
                  data = item_responses)
summary(mod_within_full)

```

```{r}
variances = VarCorr(mod_within_full, comp="Variance")
var_proid  = variances$proid[[1]]
var_item   = variances$item[[1]]
var_format = variances$format[[1]]
var_resid = attr(variances, "sc")^2
var_total = var_proid + var_item + var_format + var_resid
```

Participants account for `r round(100*var_proid/var_total, 2)` percent of the variability in response.

Items account for `r round(100*var_item/var_total, 2)` percent of the variability in response.

Format accounts for `r round(100*var_format/var_total, 2)` percent of the variability in response.

In total, `r round(100*(var_proid+var_item+var_format)/var_total, 2)` percent of the variability in response is explained.


<!-- We also plan to evaluate test-retest reliability within formats (within session and over two weeks); we expect slightly higher test-retest reliability for item wording formats that are more specific -- formats #3 and #4 above vs the use of adjectives alone. -->

<!-- We will also consider the effect on retest reliability of performance on the word recall task. -->

<!-- We will further compare response times as a function of item format using both within- and between-person data in order to evaluate the presumption that adjective ratings require less time than phrased items.  -->

<!-- Finally, secondary analyses will consider preliminary evidence for differences (e.g., mean response times, mean level of response) based on the type of device used to complete the survey (mobile, desktop, or tablet). -->

