---
title: "Descriptive statistics"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
---


```{r descriptives-1, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

```{r descriptives-2, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
library(papaja) # for pretty numbers
```

```{r descriptives-3, echo = F}
load(here("data/items_df.Rds"))
load(here("data/cleaned_data.Rds"))
```


```{r descriptives-4, echo = F}
age_dist = data %>% 
  select(age) %>% 
  summarise(across(age, list(mean = mean, 
                             sd = sd, 
                             min = min, 
                             max = max)))

sex_percent = round((table(data$sex)/nrow(data))*100,2)
ethnic_percent = round((table(data$ethnic)/nrow(data))*100,2)
```

Participants (_N_ = `r printnum(nrow(data), digits = 0)`; `r sex_percent["Female"][[1]]`\% female) were, on average, `r printnum(age_dist$age_mean[[1]])` years old (_SD_ = `r printnum(age_dist$age_sd[[1]])`, minimum = `r printnum(age_dist$age_min[[1]], digits = 0)`, maximum = `r printnum(age_dist$age_max[[1]], digits = 0)`; see Figure \@ref(fig:descriptives-5)A for the full distribution). A majority (`r ethnic_percent["White"][[1]]`\%) of participants identified as White only (`r ethnic_percent["Black"][[1]]`\% only); Figure \@ref(fig:descriptives-5)B shows the other response options and frequencies. See Figure \@ref(fig:descriptives-5)C for the distribution of education, and \@ref(fig:descriptives-5)D for the distribution of household income.

```{r descriptives-5, echo = F, fig.cap ="Distributions of key demographics across the entire sample", fig.width = 8, fig.height = 10}
age_plot = data %>% 
  ggplot(aes(x = age)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(x = "Age", y = "Frequency",
       title = "Distribution of ages") +
  theme_pubr()

edu_plot = data %>% 
  ggplot(aes(x = edu)) +
  geom_bar(stat = "count") +
  labs(x = NULL, y = "Frequency",
       title = "Distribution of education") +
  coord_flip() +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ethnic_plot = data %>% 
  ggplot(aes(x = ethnic)) +
  geom_bar(stat = "count") +
  labs(x = NULL, y = "Frequency",
       title = "Distribution of ethnicity") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hhinc_plot = data %>% 
  ggplot(aes(x = hhinc)) +
  geom_bar(stat = "count") +
  labs(x = NULL, y = "Frequency",
       title = "Distribution of household income") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggarrange(ggarrange(age_plot, ethnic_plot, nrow = 1, labels = c("A","B")),
          edu_plot,hhinc_plot, ncol = 1, labels = c(" ", "C","D"))
```


## Time

How much time elapsed between assessments?

```{r descriptives-24}
data = data %>% 
  mutate(difference = as.numeric(start_date2-start_date))
summary(data$difference)
```

How long did it take participants to complete the Time 1 survey?

```{r descriptives-25}
summary(data$duration_in_seconds/60)
```

How long did it take participants to complete the Time 2 survey?

```{r descriptives-26}
summary(data$duration_in_seconds2/60)
```


## Personality by block and format

See Table \@ref(tab:descriptives27) for the descriptive statistics of each format by block.

```{r descriptives27, echo = F}
items_df %>%
  group_by(block, format) %>%
  summarise(
    mean = mean(response),
    sd = sd(response),
    median = median(response),
    N_responses = n(),
    N_participants = length(unique(proid))
  ) %>%
  ungroup() %>%
  arrange(block, format) %>%
  kable(booktabs = T, digits = c(0,2,2,0,0,0),
        escape = F, 
        caption = "Descriptives of responses by format and block",
        col.names = c("Block", "Format", "M", "SD", "Median",
                      "N (responses)", "N (participants)")) %>%
  kable_styling() 
# %>%
#   group_rows("Block 1", 1, 4) %>%
#   group_rows("Block 2", 5, 8) %>%
  # group_rows("Block 3", 9, 12)
```

See Table \@ref(tab:descriptives-28) for the descriptive statistics of each item and format in Block 1 (Time 1).

```{r descriptives-28, results = 'asis', echo = F}
items_df %>%
  filter(block == "1") %>%
  group_by(item, format) %>%
  summarise(
    mean = mean(response),
    sd = sd(response)
  ) %>%
  mutate(value = paste0(
    printnum(mean), " (", printnum(sd), ")"
  )) %>%
  select(-mean, -sd) %>%
  spread(format, value) %>%
  kable(booktabs = T,
        caption = "Descriptives of responses to Block 1 by format and item") %>%
  kable_styling()
```


See Table \@ref(tab:descriptives-30) for the descriptive statistics of each item and format in Block 2 (Time 1).

```{r descriptives-30, results = 'asis', echo = F}
items_df %>%
  filter(block == "2") %>%
  group_by(item, format) %>%
  summarise(
    mean = mean(response),
    sd = sd(response)
  ) %>%
  mutate(value = paste0(
    printnum(mean), " (", printnum(sd), ")"
  )) %>%
  select(-mean, -sd) %>%
  spread(format, value) %>%
  kable(booktabs = T,
        caption = "Descriptives of responses to Block 2 by format and item") %>%
  kable_styling()
```

See Table \@ref(tab:descriptives-32) for the descriptive statistics of each item and format in Block 3 (Time 2).


```{r descriptives-32, results = 'asis', echo  = F}
items_df %>%
  filter(block == "2") %>%
  group_by(item, format) %>%
  summarise(
    mean = mean(response),
    sd = sd(response)
  ) %>%
  mutate(value = paste0(
    printnum(mean), " (", printnum(sd), ")"
  )) %>%
  select(-mean, -sd) %>%
  spread(format, value) %>%
  kable(booktabs = T,
        caption = "Descriptives of items to Block 3 by format") %>%
  kable_styling()
```
