---
title: "Format effects (Block 1 and 2 Data)"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

The primary aims of this study are to evaluate the effects of item wording in online, self-report personality assessment. Specifically, we intend to consider the extent to which incremental wording changes may influence differences in the distributions of responses, response times, and psychometric properties of the items. These wording changes will include a progression from using (1) trait-descriptive adjectives by themselves, (2) with the linking verb “to be” (Am…), (3) with the additional verb “to tend” (Tend to be...), and (4) with the pronoun “someone” (Am someone who tends to be…). 

Using a protocol that administers each adjective twice to the same participant (in different combinations of item format administered randomly across participants), we will use between-person analyses to compare responses using group-level data for the different formats. 

These analyses will attempt to account for memory effects by collecting data on immediate and delayed recall (5 minutes and approximately two weeks) using a memory paradigm that was developed based on a similar recall task used in the HRS (Runge et al., 2015).


```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

## Workspace

```{r}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(lme4) # for mulitlevel modeling
library(lmerTest) # for df and p-values
library(emmeans) # for pairwise comparisons
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
```

```{r, echo = F}
load(here("data/cleaned_data.Rds"))
```


## Data prep

**We will use between-person analyses to compare responses using group-level data for the different formats.**

First we select the responses to the items of different formats. For this set of analyses, we use data collected in both Block 1 and Block 2 -- that is, each participant saw the same format for every item during Block 1, but a random format for each item in Block 2.

These variable names have one of two formats: `[trait]_[abcd]` (for example, `talkative_a`) or `[trait]_[abcd]_2` (for example, `talkative_a_2`). We search for these items using regular expressions.

```{r}
items_seen_b1b2 = str_subset(
  names(data),
  "^([[:alpha:]])+_[abcd](_2)?$"
)

item_responses = data %>%
  select(proid, all_of(items_seen_b1b2), devicetype)
```

Next we reshape these data into long form.

```{r}
item_responses = item_responses %>%
  gather(item, response, -proid, -devicetype) %>%
  mutate(
    block = case_when(             # which block is the item from?
      str_detect(item, "_2") ~ "2",
      TRUE ~ "1"),
    item = str_remove(item, "_2")) %>%  # remove block id from item string
  separate(item, into = c("item", "format")) %>%
  filter(!is.na(response))
```

We also prepare a dataframe to examine the amount of time needed to respond to items. These variable names have one of two formats: `t_[trait]_[abcd]_page_submit` (for example, `t_talkative_a_page_submit`) or `t_[trait]_[abcd]_2_page_submit` (for example, `t_talkative_a_2_page_submit`). We search for these items using regular expressions.

```{r}
timing_block12 = str_subset(
  names(data),
  "^t_([[:alpha:]])+_[abcd]_(2_)?page_submit$"
)

timing_block12 = data %>%
  select(proid, all_of(timing_block12), devicetype)
```

Next we reshape these data into long form.

```{r}
timing_block12 = timing_block12 %>%
  gather(item, seconds, -proid, -devicetype) %>%
  mutate(item = str_remove(item, "^t_"),
         item = str_remove(item, "_2"),
         item = str_remove(item, "_page_submit$")) %>% 
  separate(item, into = c("item", "format")) %>%
  filter(!is.na(seconds))
```

## Response by Device

We used a multilevel model, nesting response within participant to account for dependence. Our primary predictor was device format

```{r}
mod.format = lmer(response~devicetype + (1|proid), 
                  data = item_responses)
anova(mod.format)

```

```{r, fig.cap = "Predicted response on personality items by condition."}
plot1 = plot_model(mod.format, type = "pred") 

plot1$devicetype +
  labs(x = NULL,
       y = "Average response",
       title = "Average responses by device") +
  theme_pubclean()
```

```{r, fig.cap = "Distribution of responses by category"}
means_by_group = item_responses %>%
  group_by(devicetype) %>% 
  summarise(m = mean(response),
            s = sd(response))

item_responses %>%
  ggplot(aes(x = response)) +
  geom_histogram(aes(fill = block),
                 position = "dodge",
                 bins = 6, color = "white") +
  geom_vline(aes(xintercept = m), 
             data = means_by_group) +
  facet_wrap(~devicetype, scales = "free_y") +
  #guides(fill = "none") +
  scale_x_continuous(breaks = 1:6) +
  labs(y = "Number of particpants",
       title = "Distribution of responses by format") +
  theme_pubr()
```

## Timing by device



We used a multilevel model, nesting seconds within participant to account for dependence. Our primary predictor was format.

```{r}

mod.format = lmer(seconds~devicetype + (1|proid), 
                  data = timing_block12)
anova(mod.format)
```

```{r, fig.cap = "Predicted seconds on personality items by condition."}
plot1 = plot_model(mod.format, type = "pred") 

plot1$devicetype +
  labs(x = NULL,
       y = "Seconds",
       title = "Average seconds time by device type") +
  theme_pubclean()
```

```{r, fig.cap = "Distribution of secondss by category"}
means_by_group = timing_block12 %>%
  group_by(devicetype) %>% 
  summarise(m = mean(seconds),
            s = sd(seconds))

timing_block12 %>%
  ggplot(aes(x = seconds, fill = devicetype)) +
  geom_histogram(bins = 100) +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  facet_wrap(~devicetype, scales = "free_y") +
  guides(fill = "none") +
  scale_x_log10() +
  labs(y = "Number of particpants",
       title = "Distribution of seconds by format",
       x = "Seconds (logrithmic scale)") +
  theme_pubr()
```
