---
title: "Device effects"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
---


```{r device-1, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

```{r device-2, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(glmmTMB) # for mulitlevel modeling
library(broom) # for tidying output
library(emmeans) # for pairwise comparisons
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
library(papaja) # for formatting numbers
```

```{r device-3, echo = F}
load(here("objects/cleaned_data.Rds"))
load(here("objects/items_df.Rds"))
```

In this section, we present exploratory analyses which test the effect of device type More specifically, we're interested to know whether the time it takes to complete personality assessments differs by device type (computer, phone, tablet). We also test whether the typical response to personality items is associated with device type, although we have no theoretical reasons to suspect this is the case.

For these analyses, we use only data collected in Block 1.


```{r device-4}
items_block1 = items_df %>% filter(block == "1")
```

## Demographics by device type

Device-type analyses in this project are purely exploratory, but may be hampered by potential confounds. We test whether different types of participants (based on demographic variables) used different devices to complete the survey.

```{r descriptives-14, echo = F, fig.cap = ""}
age_test_print = papaja::apa_print(
  aov(age~devicetype, data = data))
age_test = ggpubr::ggboxplot(data, "devicetype", "age") +
  stat_compare_means(comparisons = list(c("Computer", "Mobile"),
                                        c("Mobile", "Tablet"),
                                        c("Computer", "Tablet"))) +
  labs(x = NULL, y = "Age", caption = "Differences in age across device type used. We present (uncorrected) p-values showing the pairwise comparisons of average age by device type.")



sex_test = papaja::apa_print(chisq.test(table(data$sex, data$devicetype)), n = nrow(data))
```

Figure \@ref(fig:descriptives-17)A shows the distributions of age by device type; the ANOVA test of these differences is `r age_test_print$full_result$devicetype`. The chi-square test of biological sex by device type was `r sex_test$statistic`. 

```{r descriptives-17, echo = F, fig.cap ="Distributions by device type", fig.height = 12}

age_test = ggpubr::ggboxplot(data, "devicetype", "age") +
  stat_compare_means(comparisons = list(c("Computer", "Mobile"),
                                        c("Mobile", "Tablet"),
                                        c("Computer", "Tablet"))) +
  labs(x = NULL, y = "Age", caption = "Differences in age across device type used. We present (uncorrected) p-values showing the pairwise comparisons of average age by device type.")

edu_device = data %>% 
  ggplot(aes(x = edu, fill = devicetype)) +
  geom_bar(stat = "count") +
  facet_wrap(~devicetype) +
  guides(fill = "none") +
  labs(x = NULL, y = "Frequency") +
  coord_flip() +
  theme_pubr(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ethnic_device = data %>% 
  ggplot(aes(x = ethnic, fill = devicetype)) +
  geom_bar(stat = "count") +
  facet_wrap(~devicetype, scales = "free_y") +
  guides(fill = "none") +
  labs(x = NULL, y = "Frequency") +
  theme_pubr(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hhinc_device = data %>% 
  ggplot(aes(x = hhinc, fill = devicetype)) +
  geom_bar(stat = "count") +
  facet_wrap(~devicetype, scales = "free_y") +
  guides(fill = "none") +
  labs(x = NULL, y = "Frequency") +
  theme_pubr(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggarrange(age_test, edu_device, ethnic_device, hhinc_device, ncol = 1)
```


## Timing

### Timing by device

We used a multilevel model, nesting timing within participant to account for dependence. Our primary predictor was device type. As a reminder, our outcome variable (seconds) has been log-transformed, as it was strongly skewed.

```{r device-5}
mod.timing = glmmTMB(seconds_log~devicetype + (1|proid), 
                  data = items_block1)
tidy(aov(mod.timing))
```



```{r device-6, echo = F}
tD_aov = tidy(aov(mod.timing))
tD_sig = tD_aov$p.value[[1]] < .05
tD_aov = tD_aov %>% 
  as_tibble() %>% 
  mutate(across(starts_with("P"), printp),
         across(where(is.numeric), printnum))
```

Device type was `r ifelse(tD_sig, "associated", "unassociated")` with the time it took to respond to personality items $(F(`r tD_aov$df[[1]]`, `r tD_aov$df[[3]]`) = `r tD_aov$statistic[[1]]`, p = `r tD_aov$p.value[[1]]`)$.

```{r device-7, fig.cap = "Predicted timing on personality items by condition."}
plot1 = plot_model(mod.timing, type = "pred") 

plot1$devicetype +
  labs(x = NULL,
       y = "Log-seconds (per item)",
       title = "Average time per personality item\nby device type",
       caption = "Bars represent 95% confidence intervals") +
  theme_pubclean()
```

```{r device-8, fig.cap = "Distribution of secondss by category"}
means_by_group = items_block1 %>%
  group_by(devicetype) %>% 
  summarise(m = mean(timing),
            s = sd(timing))

items_block1 %>%
  ggplot(aes(x = timing, fill = devicetype)) +
  geom_histogram(bins = 100) +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  facet_wrap(~devicetype, scales = "free_y") +
  guides(fill = "none") +
  scale_x_log10() +
  labs(y = "Number of particpants",
       title = "Distribution of timing by format",
       x = "timing (logrithmic scale)") +
  theme_pubr()
```

### Device by format

We also check to see whether device type and format interact in the prediction of time to answer personality items.

```{r device-9}
mod.timing2 = glmmTMB(seconds_log~devicetype*format + (1|proid), 
                  data = items_block1)
tidy(aov(mod.timing2))
```

**Preregistration note: this model was unable to converge, likely due to the small sample size. We have code prepared to extract and print estimates of the interaction upon collecting sufficient data.**



```{r device-10, eval = F, echo = F}
tD2_aov = tidy(aov(mod.timing2))
tD2_sig = tD2_aov$p.value[[4]] < .05
tD2_aov = tD2_aov %>% 
  as_tibble() %>% 
  mutate(across(starts_with("P"), printp),
         across(where(is.numeric), printnum))

<!-- The interaction between device type and format was `r ifelse(tD2_sig, "associated", "unassociated")` with the time it took to respond to personality items $(F(`r tD2_aov$df[[4]]`, `r tD2_aov$df[[5]]`) = `r tD2_aov$statistic[[4]]`, p = `r tD2_aov$p.value[[4]]`)$. -->

```

```{r device-11, fig.cap = "Predicted timing on personality items by condition."}
plot1 = plot_model(mod.timing2, type = "pred", terms = c("format", "devicetype")) 

plot1 +
  geom_line() +
  labs(x = NULL,
       y = "Log-seconds (per item)",
       title = "Average time per personality item\nby device type and item format",
       color = "Device",
       caption = "Bars represent 95% confidence intervals") +
  theme_pubclean()
```

## Responses

Here we estimate the differences in response to personality items items by device. Again, we have no theoretical rationale for these models -- these are purely exploratory.

### Response by device

We used a multilevel model, nesting response within participant to account for dependence. Our primary predictor was device type. 

```{r device-12}
mod.responseD = glmmTMB(response~devicetype + (1|proid), 
                  data = items_block1)
tidy(aov(mod.responseD))
```



```{r device-13, echo = F}
rD_aov = tidy(aov(mod.responseD))
rD_sig = rD_aov$p.value[[1]] < .05
rD_aov = rD_aov %>% 
  as_tibble() %>% 
  mutate(across(starts_with("P"), printp),
         across(where(is.numeric), printnum))
```

When examining both Block 1 and Block 2 data, device type was `r ifelse(rD_sig, "associated", "unassociated")` with the time it took to respond to personality items $(F(`r rD_aov$df[[1]]`, `r rD_aov$df[[3]]`) = `r rD_aov$statistic[[1]]`, p = `r rD_aov$p.value[[1]]`)$.

```{r device-14, fig.cap = "Predicted response on personality items by condition."}
plot1 = plot_model(mod.responseD, type = "pred") 

plot1$devicetype +
  labs(x = NULL,
       y = "Expected response",
       title = "Expected responses by device",
       caption = "Bars represent 95% confidence intervals") +
  theme_pubclean()
```

```{r device-15, fig.cap = "Distribution of responses by category"}
means_by_group = items_block1 %>%
  group_by(devicetype) %>% 
  summarise(m = mean(response),
            s = sd(response))

items_block1 %>%
  ggplot(aes(x = response)) +
  geom_histogram(aes(fill = block),
                 position = "dodge",
                 bins = 6, color = "white") +
  geom_vline(aes(xintercept = m), 
             data = means_by_group) +
  facet_wrap(~devicetype, scales = "free_y") +
  #guides(fill = "none") +
  scale_x_continuous(breaks = 1:6) +
  labs(y = "Number of particpants",
       title = "Distribution of responses by format") +
  theme_pubr()
```

### Device by format

We also check whether item format moderated the relationship between device type and response.

```{r device-16}
mod.responseD2 = glmmTMB(response~devicetype*format + (1|proid), 
                  data = items_block1)
tidy(aov(mod.responseD2))
```

**Preregistration note: this model was unable to converge, likely due to the small sample size. We have code prepared to extract and print estimates of the interaction upon collecting sufficient data.**

```{r device-17, eval = F, echo = F}
rD2_aov = tidy(aov(mod.responseD))
rD2_sig = rD2_aov$p.value[[1]] < .05
rD2_aov = rD2_aov %>% 
  as_tibble() %>% 
  mutate(across(starts_with("P"), printp),
         across(where(is.numeric), printnum))

<!-- The interaction between device type and format was `r ifelse(rD2_sig, "associated", "unassociated")` with the time it took to respond to personality items $(F(`r rD2_aov$NumDF[[1]]`, `r rD2_aov$DenDF[[1]]`) = `r rD2_aov$Fval[[1]]`, p = `r rD2_aov$Pval[[1]]`)$. -->

```


```{r device-18, fig.cap = "Predicted response on personality items by condition."}
plot2 = plot_model(mod.responseD2, type = "pred", terms = c("format", "devicetype")) 

plot2 +
  geom_line() +
  labs(x = NULL,
       y = "Average response",
       title = "Average responses by device",
       caption = "Bars represent 95% confidence intervals") +
  theme_pubclean()
```
