---
title: "Does the internal consistency of Big Five traits vary by item wording?"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
---

We calculate and report Cronbach’s alpha for all formats using data from Block 1 only. This will include both the average split-half reliability, as well as the 95% confidence interval. Differences in internal consistency will be considered statistically significant if the confidence intervals of two formats do not overlap. We will also show the distribution of all possible split halves for each of the four formats.


```{r internal-1, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

```{r internal-2, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(glmmTMB) # for mulitlevel modeling
library(broom) # for presenting results
library(emmeans) # for comparisons
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
library(papaja) # for number formatting
library(psych) # for correlation tests
library(ggridges) # for overlay distributions

options(knitr.kable.NA = '')
```

```{r internal-3, echo = F}
load(here("objects/items_df.Rds"))
```

We start by creating a wide-format of the dataset using only the Block 1 data.

```{r internal-4}
items_wide = items_df %>%
  # only block 1 responses
  filter(block == 1) %>% 
  #only need these variables
  select(proid, condition, item, response) %>% 
  # to wide form
  spread(item, response)
```

Next, we identify the items associated with each trait. These come from the Health and Retirement Study Psychosocial and Lifestyle Questionnaire 2006-2016 user guide, which can be found at this [link](https://hrs.isr.umich.edu/publications/biblio/9066).

```{r internal-5}
Extra = c("outgoing", "friendly", "lively", "active" ,"talkative")
Agree = c("helpful", "warm", "caring", "softhearted", "sympathetic")
Consc = c("reckless", "organized", "responsible", "hardworking", "selfdisciplined", 
          "careless", "impulsive", "cautious", "thorough", "thrifty")
Neuro = c("moody", "worrying", "nervous", "calm")
Openn = c("creative", "imaginative", "intelligent", "curious", "broadminded", 
          "sophisticated", "adventurous")
```

## Calculate Cronbach's alpha for each format

We start by grouping data by condition and then nesting, to create separate data frames for each of the four formats.

```{r internal-6}
format_data = items_wide %>% 
  group_by(condition) %>% 
  nest() %>% 
  ungroup()
```

Next we create separate datasets for each of the five personality traits.

```{r internal-7}
format_data = format_data %>% 
  mutate(
    data_Extra = map(data, ~select(.x, all_of(Extra))),
    data_Agree = map(data, ~select(.x, all_of(Agree))),
    data_Consc = map(data, ~select(.x, all_of(Consc))),
    data_Neuro = map(data, ~select(.x, all_of(Neuro))),
    data_Openn = map(data, ~select(.x, all_of(Openn)))
    ) 
```

We gather these datasets into a single column, for ease of use.

```{r internal-8}
format_data = format_data %>% 
  select(-data) %>% 
  gather(variable, data, starts_with("data")) %>% 
  mutate(variable = str_remove(variable, "data_"))
```

Next we apply the `alpha` and `omega` functions to the datasets. We do not need to use the `check.keys` function, as items were reverse-scored during the cleaning process.

```{r internal-9, results = 'hide'}
format_data = format_data %>% 
  mutate(
    nvar = map_dbl(data, ncol),
    alpha = map(data, psych::alpha),
    omega = map(data, psych::omega, plot = F))
```

## Alpha 

We extract the estimated confidence intervals. (Note that these estimates are unreliable in small samples. The estimates extracted based on pilot data are not expected to reflect estimates provided in the final analyses.) The final summary of results is presented in Table \@ref(tab:internal10b) and Figure \@ref(fig:internal11).

```{r internal-10, results = 'asis'}
format_alpha = format_data %>% 
  mutate(alpha_list = map(alpha, "total"),
         alpha_est = map_dbl(alpha_list, "raw_alpha"),
         se_est = map_dbl(alpha_list, "ase"),
         lower_est = alpha_est - (1.96*se_est),
         upper_est = alpha_est + (1.96*se_est)) 
```
```{r internal10b, results = 'asis', echo = F }
format_alpha %>% 
  select(condition, nvar, variable, alpha_est, lower_est, upper_est) %>% 
  mutate(
    across(ends_with("est"), printnum),
    value = paste0(alpha_est, " [", lower_est, ", ", upper_est, "]")) %>% 
  select(-contains("est")) %>% 
  spread(condition, value) %>%
  mutate(variable = factor(variable,
                           levels = c("Extra", "Agree", "Consc", "Neuro", "Openn"),
                           labels = c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>% 
  arrange(variable) %>% 
  mutate(label = paste0(variable, " (", nvar, " descriptors)")) %>% 
  select(label, A:D) %>% 
  kable(booktabs = T,
        caption = "Cronbach's alpha across format and trait.") %>% 
  kable_styling()
```

```{r internal11, echo = F, fig.cap = "Estimates of Cronbach's alpha across format and trait."}
format_alpha %>% 
  mutate(cond_num = case_when(
    condition == "A" ~ 1,
    condition == "B" ~ 2,
    condition == "C" ~ 3,
    condition == "D" ~ 4
  )) %>% 
  ggplot(aes(x = cond_num, y = alpha_est)) +
  geom_errorbar(aes(ymin = lower_est, ymax = upper_est)) +
  geom_point() +
  geom_line(alpha = .3) +
  scale_x_continuous(breaks = c(1:4),
                     labels = c("A","B","C","D"))+
  labs(x = NULL, y = "Alpha") +
  facet_wrap(~variable) +
  theme_pubclean()
```

## Split-half reliability
Alpha is the average split-half reliability; given space, it can be useful to report the distribution of all split-half reliability estimates. We use the `splitHalf` function to calculate those. We use smoothed correlation matrices here because when developing code on the pilot data, we had non-positive definite correlation matrices. See Figure \@ref(fig:internal12b) for these distributions. 

```{r internal-12}
format_split = format_data %>% 
  mutate(cor_mat = map(data, cor),
         cor_mat = map(cor_mat, cor.smooth)) %>% 
  mutate(splithalf = map(cor_mat, splitHalf, raw = T))
```

```{r internal12b, echo = F, fig.cap = "Distribution of split-half reliabilities"}
format_split %>% 
  mutate(sh_est = map(splithalf, "raw")) %>% 
  select(variable, condition, sh_est) %>% 
  unnest(cols = c(sh_est)) %>% 
  ggplot(aes(x = sh_est, y = condition, fill = condition)) +
  geom_density_ridges() +
  facet_wrap(~variable) +
  labs(x = "Internal consistency",
       y = NULL) +
  guides(fill = "none") +
  theme_pubclean()
```


## Omega

We extract the estimated confidence intervals. (Note that these estimates are unreliable in small samples. The estimates extracted based on pilot data are not expected to reflect estimates provided in the final analyses.) The final summary of results is presented in Table \@ref(tab:internal10b) and Figure \@ref(fig:internal11).

```{r internal-13, results = 'asis'}
format_omega = format_data %>% 
  mutate(omega_h = map_dbl(omega, "omega_h")) 
```

```{r internal13b, results = 'asis', echo = F }
format_omega %>% 
  select(condition, nvar, variable, omega_h) %>% 
  mutate(omega_h = printnum(omega_h)) %>% 
  spread(condition, omega_h) %>%
  mutate(variable = factor(variable,
                           levels = c("Extra", "Agree", "Consc", "Neuro", "Openn"),
                           labels = c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>% 
  arrange(variable) %>% 
  mutate(label = paste0(variable, " (", nvar, " descriptors)")) %>% 
  select(label, A:D) %>% 
  kable(booktabs = T,
        caption = "Omega hierarchical across format and trait.") %>% 
  kable_styling()
```

```{r internal13c, echo = F, fig.cap = "Estimates of omega hierarchical across format and trait."}
format_omega %>% 
  mutate(cond_num = case_when(
    condition == "A" ~ 1,
    condition == "B" ~ 2,
    condition == "C" ~ 3,
    condition == "D" ~ 4
  )) %>% 
  ggplot(aes(x = cond_num, y = omega_h, color = variable)) +
  geom_point() +
  geom_line(alpha = .5) +
  labs(x = NULL, y = "Omega H") +
  scale_x_continuous(breaks = c(1:4), labels = c("A","B","C","D")) +
  theme_pubclean()
```