---
title: "Power analysis"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
---

```{r power1, echo = F, include = F}
knitr::opts_chunk$set(warning = F, message = F)
run_analyses = TRUE
```

```{r, echo = F}
library(here)
library(tidyverse)
library(pwr)
load(here("objects/block1_coded.Rds"))
```


We conduct power analyses for the research question, "Does item format influence expected response to personality items?" by powering a balanced one-way analysis of variance. This model assumes no individual differences in response, thereby providing a more conservative estimate of the sample size needed.

```{r}
# calculate each individual's average response
means = item_block1 %>% 
  group_by(proid, condition) %>% 
  summarise(response = mean(response)) %>% 
  ungroup() 

# calculate mean and variance for each condition
means = means %>% 
  group_by(condition) %>%
  summarise(m = mean(response),
            v = var(response),
            n = n()) 

# calculate ewighted variance
weighted_var = means %>% 
  mutate(newv = v*(n-1)) %>% 
  select(newv, n) %>% 
  colSums() 
weighted_var = weighted_var[[1]]/(weighted_var[[2]]-4)

# enter information into power function
power.anova.test(groups = 4, 
                 between.var = var(means$m), 
                 within.var = weighted_var,
                 power = .9, 
                 sig.level = .05)
```

This analysis suggests that 136 participants are needed in each condition to achieve 90% power for the differences in means found in the pilot data. To be safe, we plan to recruit 250 participants per condition.


