---
title: "Power analysis"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
---

```{r, echo = F}
run_analyses = FALSE
```


We conduct power analyses for the main research question -- does formatting affect response to personality items -- using a simulation method. That is, we generate datasets of varying sample sizes (from as few as 50 participants per condition to as many as 100), then simulate responses based on the models fit to the pilot data. 

```{r, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(lme4) # for mulitlevel modeling
library(lmerTest) # for p-values
library(ggpubr) # for prettier plots
```

Here we set the sample sizes we'll test, as well as the number of simulations we'll run for each sample size.

```{r}
sample_sizes = seq(50, 500, 25)

n_sims = 1000
```


## Using Block 1 data

To simplify our code, we write a function that simulates responses to model 1 based on a given sample size, N, and number of repetitions.

```{r, echo = F}
load(here("objects/mod_format_b1.Rdata"))
```


```{r}
# function to simulate mod.format_b1

sim_format_b1 = function(n, sims){
  p_vals = numeric(length = sims)
  
  sim_a = expand_grid(
    proid = as.character(1:n),
    item = c(1:33),
    format = "Adjective\nOnly"
  )

  sim_b = expand_grid(
    proid = as.character((n+1):(2*n)),
    item = c(1:33),
    format = "Am\nAdjective"
  )
  
  sim_c = expand_grid(
    proid = as.character(((2*n)+1):(3*n)),
    item = c(1:33),
    format = "Tend to be\nAdjective"
  )
  sim_d = expand_grid(
    proid = as.character(((3*n)+1):(4*n)),
    item = c(1:33),
    format = "Am someone\nwho tends to be\nAdjective"
  )
  
  sim_data = rbind(sim_a, sim_b) %>% rbind(sim_c) %>% rbind(sim_d)
  for (i in 1:sims){
    sim_data$response = simulate(mod.format_b1, newdata = sim_data, allow.new.levels = T)[,1]
    sim_mod = lmer(response~format + (1|proid), data = sim_data)
    p_vals[i] = anova(sim_mod)["format", 6]}
  return(p_vals)
}
```

Next we identify the sample sizes for simulation (from 50 to 500 by 25) and create a data frame to hold the results. Power represents the proportion of simulations for which _p_ is less than .05.

```{r}
# simulate at various sample sizes
power_df = data.frame(
  N = sample_sizes,
  power = 0
)
```

Here we (inefficiently) loop through all sample sizes and calculate power. Final results are presented in Figure \@ref(fig:plotpower1).

```{r, eval = run_analyses}
set.seed(20210729)
for(i in sample_sizes){
  pvalues = sim_format_b1(i, n_sims)
  sig = ifelse(pvalues < .05, 1, 0)
  power_df$power[power_df$N == i] <- sum(sig)/n_sims
}
```

```{r, echo = F, eval = run_analyses}
save(power_df, file = here("objects/power_format_b1.Rdata"))
```

```{r, echo = F}
load(here("objects/power_format_b1.Rdata"))
```

```{r plotpower1, echo = F, fig.cap = "Simulated power by sample size per condition for Block 1 in Time 1"}
power_df %>% 
  ggplot(aes(x = N, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    x = "N per condition",
    y = "Simulated power"
  ) +
  theme_pubclean()
```

```{r}
#identify minimum sample size

power_df_min = power_df %>% 
  filter(power > .95)

N_min = min(power_df_min$N)
```

The simulation suggests that power would be over the threshold of .95 with a sample size of `r N_min` participants per condition.

## Using Block 1 and 2 data

Here we repeat the process for our second model, which uses both blocks of data from Time 1 (i.e., Blocks 1 and 2).

```{r, echo = F}
load(here("objects/mod_format_b2.Rdata"))
```


```{r}
# function to simulate mod.format_b2

sim_format_b2 = function(n, sims){
  p_vals = numeric(length = sims)
  
  sim_a_b2 = expand_grid(
    proid = as.character(1:n),
    item = c(1:33),
    format = "Adjective\nOnly",
    block = "1"
  )

  sim_b_b2 = expand_grid(
    proid = as.character((n+1):(2*n)),
    item = c(1:33),
    format = "Am\nAdjective",
    block = "1"
  )
  
  sim_c_b2 = expand_grid(
    proid = as.character(((2*n)+1):(3*n)),
    item = c(1:33),
    format = "Tend to be\nAdjective",
    block = "1"
  )
  sim_d_b2 = expand_grid(
    proid = as.character(((3*n)+1):(4*n)),
    item = c(1:33),
    format = "Am someone\nwho tends to be\nAdjective",
    block = "1"
  )
  sim_b2 = expand_grid(
    proid = as.character(1:(4*n)),
    item = c(1:33),
    block = "2"
  )
  sim_b2$format = sample(
    x = c("Adjective\nOnly",
          "Am\nAdjective",
          "Tend to be\nAdjective",
          "Am someone\nwho tends to be\nAdjective"), 
    size = 33*n*4,
    replace = TRUE
  )
  
  sim_data = full_join(sim_a_b2, sim_b_b2) %>% 
    full_join(sim_c_b2) %>% 
    full_join(sim_d_b2) %>% 
    full_join(sim_b2)
  
  for (i in 1:sims){
    sim_data$response = simulate(mod.format_b2, 
                                 newdata = sim_data, 
                                 allow.new.levels = T)[,1]
    sim_mod = lmer(response~format + (1|proid), 
                   data = sim_data)
    p_vals[i] = anova(sim_mod)["format", 6]}
  return(p_vals)
}
```

We use the same sample sizes and simulation length for these analyses, so we start by creating a new data frame.

```{r}
power_df_2 = data.frame(
  N = sample_sizes,
  power = 0
)
```

Here we (inefficiently) loop through all sample sizes and calculate power. Final results are depicted in Figure \@ref(fig:plotpower2).

```{r, eval = run_analyses}
set.seed(20210729)
for(i in sample_sizes){
  pvalues = sim_format_b2(i, n_sims)
  sig = ifelse(pvalues < .05, 1, 0)
  power_df_2$power[power_df_2$N == i] <- sum(sig)/n_sims
}
```

```{r, echo = F, eval = run_analyses}
save(power_df_2, file = here("objects/power_format_b2.Rdata"))
```

```{r, echo = F}
load(here("objects/power_format_b2.Rdata"))
```


```{r plotpower2, echo =F, fig.cap = "Simulated power by sample size per condition for Blocks 1 and 2 in Time 1"}
power_df_2 %>% 
  ggplot(aes(x = N, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    x = "N per condition",
    y = "Simulated power"
  ) +
  theme_pubclean()
```

```{r}
#identify minimum sample size

power_df2_min = power_df_2 %>% 
  filter(power > .95)

N_min2 = min(power_df2_min$N)
```

The simulation suggests that power would be over the threshold of .95 with a sample size of `r N_min2` participants per condition.

