---
title: "Does item format impact experience?"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
---

These analyses test whether item format affects participants' subjective experiences of participating in personality surveys. 

```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

```{r, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(effectsize) # for effect sizes
library(janitor) # for variable names
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
library(papaja) # pretty numbers
library(emmeans)
```

```{r, echo = F}
load(here("objects/enjoy_df.Rds"))
```

## Enjoyment

First, we test whether participants enjoyed their experience as a function of format. The item participants rated was:

"Overall, I am enjoying responding to the present survey."

```{r}
mod_enjoy_1 = lm(enjoy_responding ~ format, data = enjoy_df)
car::Anova(mod_enjoy_1)
```

```{r}
effectsize::hedges_g(
  enjoy_responding ~ format, 
  data = filter(enjoy_df, format %in% c("Adjective\nOnly", "Am\nAdjective")
))

effectsize::hedges_g(
  enjoy_responding ~ format, 
  data = filter(enjoy_df, format %in% c("Adjective\nOnly", "Tend to be\nAdjective")))

effectsize::hedges_g(
  enjoy_responding ~ format, 
  data = filter(enjoy_df, format %in% c("Adjective\nOnly", "Am someone\nwho tends to be\nAdjective")
))

effectsize::hedges_g(
  enjoy_responding ~ format, 
  data = filter(enjoy_df, format %in% c("Am\nAdjective", "Tend to be\nAdjective")
))

effectsize::hedges_g(
  enjoy_responding ~ format, 
  data = filter(enjoy_df, format %in% c("Am\nAdjective", "Am someone\nwho tends to be\nAdjective")
))

effectsize::hedges_g(
  enjoy_responding ~ format, 
  data = filter(enjoy_df, format %in% c("Tend to be\nAdjective", "Am someone\nwho tends to be\nAdjective")
))
```

Participants did not vary in their enjoyment of the survey as a function of item format. See \@ref(fig:enjoyFormat).

```{r enjoyFormat, fig.cap = "Predicted enjoyment by item format"}
plot_model(mod_enjoy_1, type = "pred", show.data = T, jitter = T) +
  labs(x = NULL,
       y = "Average enjoyment",
       title = NULL)
```

We also test whether this is a function of device type and the interaction of device type with format. 

```{r}
mod_enjoy_2 = lm(enjoy_responding ~ devicetype, data = enjoy_df)
car::Anova(mod_enjoy_2)
```

Participants did not enjoy differently by device type. 

```{r}
hedges_g(
  enjoy_responding ~ devicetype, 
  data = filter(enjoy_df,
    devicetype %in% c("Tablet (for example, iPad, Galaxy Tablet, Amazon Fire, etc.)", "Mobile")))


hedges_g(
  enjoy_responding ~ devicetype, 
  data = filter(enjoy_df,
    devicetype %in% c("Tablet (for example, iPad, Galaxy Tablet, Amazon Fire, etc.)", "Desktop or laptop computer"))
)

hedges_g(
  enjoy_responding ~ devicetype, 
  data = filter(enjoy_df,
    devicetype %in% c("Mobile", "Desktop or laptop computer"))
)
```

```{r}
mod_enjoy_3 = lm(enjoy_responding ~ format*devicetype, data = enjoy_df)
car::Anova(mod_enjoy_3, type = "3")
```

The relationship of item format to enjoyment did not vary as a function of device type.

## Perception of survey design

Next, we test whether participants viewed the survey differently as a function of format. The item participants rated was:

"Overall, I think the present survey is well designed."

```{r}
mod_design_1 = lm(well_designed_study ~ format, data = enjoy_df)
car::Anova(mod_design_1)
```

```{r}
hedges_g(
  well_designed_study ~ format, 
  data = filter(enjoy_df, format %in% c("Adjective\nOnly", "Am\nAdjective")))

hedges_g(
  well_designed_study ~ format, 
  data = filter(enjoy_df, format %in% c("Adjective\nOnly", "Tend to be\nAdjective")))

hedges_g(
  well_designed_study ~ format, 
  data = filter(enjoy_df, format %in% c("Adjective\nOnly", "Am someone\nwho tends to be\nAdjective")))

hedges_g(
  well_designed_study ~ format, 
  data = filter(enjoy_df, format %in% c("Am\nAdjective", "Tend to be\nAdjective")))

hedges_g(
  well_designed_study ~ format, 
  data = filter(enjoy_df, format %in% c("Am\nAdjective", "Am someone\nwho tends to be\nAdjective")))

hedges_g(
  well_designed_study ~ format, 
  data = filter(enjoy_df, format %in% c("Tend to be\nAdjective", "Am someone\nwho tends to be\nAdjective")))
```

Participants did not vary in their perception of the survey as a function of device type. See \@ref(fig:designFormat).

```{r designFormat, fig.cap = "Predicted design perception by item format"}
plot_model(mod_design_1, type = "pred", show.data = T, jitter = T) +
  labs(x = NULL,
       y = "Average perception",
       title = NULL)
```

We also test whether this is a function of device type and the interaction of devicetype with format. 

```{r}
mod_design_2 = lm(well_designed_study ~ devicetype, data = enjoy_df)
car::Anova(mod_design_2)
```

Participants did perceive the design of the study differently by format. We explore this more here:

```{r}
hedges_g(
  well_designed_study ~ devicetype, 
  data = filter(enjoy_df,
    devicetype %in% c("Tablet (for example, iPad, Galaxy Tablet, Amazon Fire, etc.)", "Mobile")))

hedges_g(
  well_designed_study ~ devicetype, 
  data = filter(enjoy_df,
    devicetype %in% c("Tablet (for example, iPad, Galaxy Tablet, Amazon Fire, etc.)", "Desktop or laptop computer"))
)

hedges_g(
  well_designed_study ~ devicetype, 
  data = filter(enjoy_df,
    devicetype %in% c("Mobile", "Desktop or laptop computer"))
)
```

```{r}
emmeans(mod_design_2, pairwise~"devicetype", adjust = "none")
emmeans(mod_design_2, pairwise~"devicetype", adjust = "holm")
```

Participants perceive the design to be better on mobile devices than on desktop or laptop computers; however, after correcting for multiple comparisons, this effect is no longer significant.

```{r}
mod_design_3 = lm(well_designed_study ~ format*devicetype, data = enjoy_df)
car::Anova(mod_design_3, type = "3")
```

The relationship of item format to survey design enjoyment did not vary as a function of device type.
