---
title: "Does item format impact timing?"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---


```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```


```{r, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(lme4) # for mulitlevel modeling
library(lmerTest) # for p-values
library(emmeans) # for comparisons
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tables
library(papaja) # for formatting numbers
```

```{r, echo = F}
load(here("data/items_df.Rds"))
load(here("data/reverse_vector.Rds"))
```


## Analysis: Block 1 data only

We used a multilevel model, nesting log-seconds within participant to account for dependence. Our primary predictor was format. Here, we use only Block 1 data.

```{r}
item_block1 = filter(items_df, block == "1")

mod.format_b1 = lmer(seconds_log~format + (1|proid), 
                  data = item_block1)
anova(mod.format_b1)
```

```{r, fig.cap = "Predicted seconds (log) on personality items by condition, using only Block 1 data."}
plot_b1 = plot_model(mod.format_b1, type = "pred") 

plot_b1$format +
  labs(x = NULL,
       y = "Average time (log seconds)",
       title = "Average time by item formatting (Block 1 Data)") +
  theme_pubclean()
```

```{r, fig.cap = "Predicted seconds on personality items by condition, using only Block 1 data."}
plot_b1$format$data %>% 
  mutate(predicted = exp(predicted),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  mutate(x = factor(x, 
                    labels = c("Adjective\nOnly", 
                               "Am\nAdjective", 
                               "Tend to be\nAdjective", 
                               "I am someone\nwho tends to be\nAdjective"))) %>% 
  ggplot(aes(x = x, y = predicted)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  labs(x = NULL, y = "seconds", title = "Average time by item formatting (Block 1 Data)") +
  theme_pubclean()
```


```{r, fig.cap = "Distribution of time by category, block 1 data only"}
means_by_group = item_block1 %>%
  group_by(format) %>% 
  summarise(m = mean(seconds_log),
            s = sd(seconds_log))

item_block1 %>%
  ggplot(aes(x = seconds_log, fill = format)) +
  geom_histogram(bins = 50, color = "white") +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  geom_text(aes(x = 1, 
                y = 40, 
                label = paste("M =", round(m,2), 
                              "\nSD =", round(s,2))), 
            data = means_by_group, 
            hjust =0, 
            vjust = 1) +
  facet_wrap(~format) +
  guides(fill = "none") +
  labs(x = "Log-seconds",
    y = "Number of particpants",
       title = "Distribution of log-seconds by format (Block 1 data)") +
  theme_pubr()
```

#### Pairwise comparisons

```{r, results = 'asis'}
pairs(emmeans(mod.format_b1, "format"), adjust = "holm") %>% 
  kable(booktabs = T, digits = c(0, 2,2,1,2,3)) %>% 
  kable_styling()
```


### One model for each adjective

We can also repeat this analysis separately for each trait. 

```{r, results = 'asis'}
mod_by_item_b1 = item_block1 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lm(seconds_log~format, data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()

summary_by_item_b1 = mod_by_item_b1 %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm")) 

summary_by_item_b1 %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>% 
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2,
        booktabs = T, 
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df", "F", "raw", "adj"),
        caption = "Format effects on log-seconds by item (block 1 data only)") %>%
  kable_styling()
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r}
sig_item_b1 = summary_by_item_b1 %>%
  filter(p.value < .05) 

sig_item_b1 = sig_item_b1$item
sig_item_b1
```

Then we create models for each adjective. We use the `emmeans` package to perform pairwise comparisons, again with a Holm correction on the _p_-values. We also plot the means and 95% confidence intervals of each mean. 

**This code will have to be changed after final data collection. It is not self-adapting!**


### Helpful

```{r, results = 'asis'}
helpful_model_b1 = item_block1 %>%
  filter(item == "helpful") %>%
  lm(seconds_log~format, data = .)

helpful_em_b1 = emmeans(helpful_model_b1, "format")
pairs(helpful_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Helpful by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"helpful\" by format (block 1 data only)" }
plot_model(helpful_model_b1, type = "pred", terms = c("format"))
```

### Caring

```{r, results = 'asis'}
caring_model_b1 = item_block1 %>%
  filter(item == "caring") %>%
  lm(seconds_log~format, data = .)

caring_em_b1 = emmeans(caring_model_b1, "format")
pairs(caring_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Caring by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"caring\" by format (block 1 data only)" }
plot_model(caring_model_b1, type = "pred", terms = c("format"))
```

### Soft-hearted

```{r, results = 'asis'}
softhearted_model_b1 = item_block1 %>%
  filter(item == "softhearted") %>%
  lm(seconds_log~format, data = .)

softhearted_em_b1 = emmeans(softhearted_model_b1, "format")
pairs(softhearted_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Soft-hearted by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"softhearted\" by format (block 1 data only)" }
plot_model(softhearted_model_b1, type = "pred", terms = c("format"))
```

### Calm

```{r, results = 'asis'}
calm_model_b1 = item_block1 %>%
  filter(item == "calm") %>%
  lm(seconds_log~format, data = .)

calm_em_b1 = emmeans(calm_model_b1, "format")
pairs(calm_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Calm by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"calm\" by format (block 1 data only)" }
plot_model(calm_model_b1, type = "pred", terms = c("format"))
```

### Sympathetic

```{r, results = 'asis'}
sympathetic_model_b1 = item_block1 %>%
  filter(item == "sympathetic") %>%
  lm(seconds_log~format, data = .)

sympathetic_em_b1 = emmeans(sympathetic_model_b1, "format")
pairs(sympathetic_em_b1, adjust = "holm") %>%
   as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Sympathetic by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"sympathetic\" by format (block 1 data only)" }
plot_model(sympathetic_model_b1, type = "pred", terms = c("format"))
```

### Adventurous

```{r, results = 'asis'}
adventurous_model_b1 = item_block1 %>%
  filter(item == "adventurous") %>%
  lm(seconds_log~format, data = .)

adventurous_em_b1 = emmeans(adventurous_model_b1, "format")
pairs(adventurous_em_b1, adjust = "holm") %>%
   as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Adventurous by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"adventurous\" by format (block 1 data only)" }
plot_model(adventurous_model_b1, type = "pred", terms = c("format"))
```


## Analysis: Block 1 and Block 2

We used a multilevel model, nesting log-seconds within participant to account for dependence. Our primary predictor was format. Here, we use data from blocks 1 and 2.

```{r}
items_12 = items_df %>% filter(block %in% c("1","2"))
```


```{r}
mod.format_b2 = lmer(seconds_log~format + (1|proid), 
                  data = items_12)
anova(mod.format_b2)
```

```{r, fig.cap = "Predicted log-seconds on personality items by condition, using only Block 1 data."}
plot_b2 = plot_model(mod.format_b2, type = "pred") 

plot_b2$format +
  labs(x = NULL,
       y = "Average log-seconds",
       title = "Average responses by item formatting (Block 1 and Block 2)") +
  theme_pubclean()
```


```{r, fig.cap = "Predicted seconds on personality items by condition, using only Block 1 data."}
plot_b2$format$data %>% 
  mutate(predicted = exp(predicted),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  mutate(x = factor(x, 
                    labels = c("Adjective\nOnly", 
                               "Am\nAdjective", 
                               "Tend to be\nAdjective", 
                               "I am someone\nwho tends to be\nAdjective"))) %>% 
  ggplot(aes(x = x, y = predicted)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  labs(x = NULL, y = "seconds", title = "Average time by item formatting (Block 1 and Block 2)") +
  theme_pubclean()
```

```{r, fig.cap = "Distribution of log-seconds by category, block 1 and block 2"}
means_by_group = items_12 %>%
  group_by(format) %>% 
  summarise(m = mean(seconds_log),
            s = sd(seconds_log))

items_12 %>%
  ggplot(aes(x = seconds_log, fill = format)) +
  geom_histogram(bins = 100, color = "white") +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  geom_text(aes(x = 1, 
                y = 50, 
                label = paste("M =", round(m,2), 
                              "\nSD =", round(s,2))), 
            data = means_by_group, 
            hjust =0, 
            vjust = 1) +
  facet_wrap(~format) +
  guides(fill = "none") +
  labs(y = "Number of particpants",
       title = "Distribution of responses by format (Block 1 and Block 2)") +
  theme_pubr()
```

#### Pairwise comparisons

```{r, results = 'asis'}
pairs(emmeans(mod.format_b2, "format"), adjust = "holm") %>% 
  kable(booktabs = T, digits = c(0, 2,2,1,2,3)) %>% 
  kable_styling()
```

### One model for each adjective

We can also repeat this analysis separately for each trait. 

```{r, results = 'asis'}
mod_by_item_b2 = items_12 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lmer(seconds_log~format + (1|proid), data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()

summary_by_item_b2 = mod_by_item_b2 %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm")) 

summary_by_item_b2 %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>% 
  select(item, reverse, sumsq, meansq, NumDF, DenDF, statistic, p.value, p.adj) %>% 
  kable(digits = 2, 
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df1", "df2", "F", "raw", "adj"),
        booktabs = T, 
        caption = "Format effects on log-seconds by item (block 1 data only)") %>%
  kable_styling()
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r}
sig_item_b2 = summary_by_item_b2 %>%
  filter(p.value < .05) 

sig_item_b2 = sig_item_b2$item
sig_item_b2
```

Then we create models for each adjective. We use the `emmeans` package to perform pairwise comparisons, again with a Holm correction on the _p_-values. We also plot the means and 95% confidence intervals of each mean. 

**This code will have to be changed after final data collection. It is not self-adapting!**

### Helfpul

```{r, results = 'asis'}
helpful_model_b2 = items_12 %>%
  filter(item == "helpful") %>%
  lmer(seconds_log~format + (1|proid), 
                               data = .)

helpful_em_b2 = emmeans(helpful_model_b2, "format")
pairs(helpful_em_b2, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Helpful by format (Block 1 and Block 2)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"helpful\" by format (Block 1 and Block 2)" }
plot_model(helpful_model_b2, type = "pred", terms = c("format"))
```

### Caring

```{r, results = 'asis'}
caring_model_b2 = items_12 %>%
  filter(item == "caring") %>%
  lmer(seconds_log~format + (1|proid), 
                               data = .)

caring_em_b2 = emmeans(caring_model_b2, "format")
pairs(caring_em_b2, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Caring by format (Block 1 and Block 2)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"caring\" by format (Block 1 and Block 2)" }
plot_model(caring_model_b2, type = "pred", terms = c("format"))
```


### Adventurous

```{r, results = 'asis'}
adventurous_model_b2 = items_12 %>%
  filter(item == "adventurous") %>%
  lmer(seconds_log~format + (1|proid), 
                               data = .)

adventurous_em_b2 = emmeans(adventurous_model_b2, "format")
pairs(adventurous_em_b2, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Adventurous by format (Block 1 and Block 2)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r, fig.cap = "Average log-seconds to \"adventurous\" by format (Block 1 and Block 2)" }
plot_model(adventurous_model_b2, type = "pred", terms = c("format"))
```

## Analysis: Account for memory effects

```{r}
mod.format_mem = lmer(seconds_log~format*delayed_memory + (1|proid), 
                  data = items_12)
anova(mod.format_mem)
summary(mod.format_mem)
```

```{r, fig.cap = "Predicted log-seconds on personality items by condition after controlling for delayed_memory."}
plot_mem = plot_model(mod.format_mem, 
           type = "pred", 
           term = c("format", "delayed_memory[meansd]")) +
  geom_line() +
  labs(x = NULL, 
       y = "Average log-seconds") +
  scale_color_discrete("Memory", labels = c("-1SD", "Mean", "+1SD"))+
  theme_pubclean()

plot_mem
```

```{r, fig.cap = "Predicted seconds on personality items by condition after controlling for delayed_memory.", fig.width = 8}
plot_mem$data %>% as_tibble %>% 
  mutate(predicted = exp(predicted),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high),
         group_col = factor(group_col, labels = c("Memory\n-1SD", "Memory\nMean", "Memory\n+1SD"))) %>% 
  mutate(x = factor(x, 
                    labels = c("Adjective\nOnly", 
                               "Am\nAdjective", 
                               "Tend to be\nAdjective", 
                               "I am someone\nwho tends to be\nAdjective"))) %>% 
  ggplot(aes(x = x, y = predicted, color = group_col)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  labs(x = NULL, y = "seconds", title = "Average time by item formatting (Block 1 and Block 2)") +
  facet_wrap(~group_col) + 
  guides(color = "none") +
  theme_pubclean()
```

### One model for each adjective

```{r, results = 'asis'}
mod_by_item_mem = items_12 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lmer(seconds_log~format*delayed_memory + (1|proid), data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()

summary_by_item_mem = mod_by_item_mem %>% 
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format:delayed_memory") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_mem %>%
  arrange(reverse, item) %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, NumDF, DenDF, statistic, p.value, p.adj) %>% 
  kable(digits = 2, booktabs = T) %>%
  kable_styling()
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r}
sig_item_mem = summary_by_item_mem %>%
  filter(p.value < .05) 

sig_item_mem = sig_item_mem$item
sig_item_mem
```

### Outgoing

```{r, results = 'asis'}
outgoing_model_mem = items_12 %>%
  filter(item == "outgoing") %>%
  lmer(seconds_log~format*delayed_memory + (1|proid), 
                               data = .)
```

```{r, fig.cap = "Average log-seconds to \"outgoing\" by format (Block 1 and Block 2)" }
plot_model(outgoing_model_mem, type = "pred", terms = c("format", "delayed_memory[meansd]"))
```

### Warm

```{r, results = 'asis'}
warm_model_mem = items_12 %>%
  filter(item == "warm") %>%
  lmer(seconds_log~format*delayed_memory + (1|proid), 
                               data = .)
```

```{r, fig.cap = "Average log-seconds to \"warm\" by format (Block 1 and Block 2)" }
plot_model(warm_model_mem, type = "pred", terms = c("format", "delayed_memory[meansd]"))
```

### Responsible

```{r, results = 'asis'}
responsible_model_mem = items_12 %>%
  filter(item == "responsible") %>%
  lmer(seconds_log~format*delayed_memory + (1|proid), 
                               data = .)
```

```{r, fig.cap = "Average log-seconds to \"responsible\" by format (Block 1 and Block 2)" }
plot_model(responsible_model_mem, type = "pred", terms = c("format", "delayed_memory[meansd]"))
```

### Imaginative

```{r, results = 'asis'}
imaginative_model_mem = items_12 %>%
  filter(item == "imaginative") %>%
  lmer(seconds_log~format*delayed_memory + (1|proid), 
                               data = .)
```

```{r, fig.cap = "Average log-seconds to \"imaginative\" by format (Block 1 and Block 2)" }
plot_model(imaginative_model_mem, type = "pred", terms = c("format", "delayed_memory[meansd]"))
```

### Talkative

```{r, results = 'asis'}
talkative_model_mem = items_12 %>%
  filter(item == "talkative") %>%
  lmer(seconds_log~format*delayed_memory + (1|proid), 
                               data = .)
```

```{r, fig.cap = "Average log-seconds to \"talkative\" by format (Block 1 and Block 2)" }
plot_model(talkative_model_mem, type = "pred", terms = c("format", "delayed_memory[meansd]"))
```

### Sophisticated

```{r, results = 'asis'}
sophisticated_model_mem = items_12 %>%
  filter(item == "sophisticated") %>%
  lmer(seconds_log~format*delayed_memory + (1|proid), 
                               data = .)
```

```{r, fig.cap = "Average log-seconds to \"sophisticated\" by format (Block 1 and Block 2)" }
plot_model(sophisticated_model_mem, type = "pred", terms = c("format", "delayed_memory[meansd]"))
```

## Inclusion of "I" (Block 1 and Block 3)

We used a multilevel model, nesting response within participant to account for dependence. Our primary predictors are format and also the presence of the word "I". Here, we use data from blocks 1 and 3.

```{r}
items_13 = items_df %>% 
  filter(block %in% c("1","3")) %>% 
  filter(condition != "A") %>% 
  filter(time2 == "yes")
```

```{r}
mod.format_b3_1 = lmer(seconds_log~format + i + (1|proid), 
                  data = items_13)
anova(mod.format_b3_1)

mod.format_b3_2 = lmer(seconds_log~format*i + (1|proid), 
                  data = items_13)
anova(mod.format_b3_2)
```

```{r, fig.cap = "Predicted log-seconds on personality items by condition and I, using Block 1 and Block 3 data."}
plot_b2 = plot_model(mod.format_b3_2, type = "pred", terms = c("format", "i")) 

plot_b2 +
  labs(x = NULL,
       y = "Average log-seconds",
       title = "Average responses by item formatting (Block 1 and Block 3)",
       color = "I") +
  theme_pubclean()
```

### One model for each adjective

```{r, results = 'asis'}
mod_by_item_i1 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lmer(seconds_log~format+i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()

summary_by_item_i1 = mod_by_item_i1 %>% 
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_i1 %>%
  arrange(reverse, item) %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, NumDF, DenDF, statistic, p.value, p.adj) %>% 
  kable(digits = 2, booktabs = T) %>%
  kable_styling()
```


```{r, results = 'asis'}
mod_by_item_i2 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lmer(seconds_log~format*i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()

summary_by_item_i2 = mod_by_item_i2 %>% 
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format:i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_i2 %>%
  arrange(reverse, item) %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, NumDF, DenDF, statistic, p.value, p.adj) %>% 
  kable(digits = 2, booktabs = T) %>%
  kable_styling()
```