---
title: "Does item format impact timing?"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    always_allow_html: true
---


```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```


```{r, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(glmmTMB) # for mulitlevel modeling
library(broom) # for tidying
library(emmeans) # for comparisons
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tablesgi
library(papaja) # for formatting numbers
```

```{r, echo = F}
load(here("objects/items_df.Rds"))
load(here("objects/reverse_vector.Rds"))
```


## Effect of format on timing (Blocks 1 and 2 data)

We used a multilevel model, nesting log-seconds within participant to account for dependence. Our primary predictor was format. Here, we use only Block 1 data. Results are depicted in Figure \@ref(fig:timingmod1). The full distribution of timing (in log-seconds) is shown in Figure \@ref(fig:timingdist). Tests of pairwise comparisons are shown in Table \@ref(tab:pairwiseTab).

```{r}
item_block12 = filter(items_df, block %in% c("1", "2")) %>% 
  filter(!is.infinite(seconds_log)) # this was added post pre-registration

mod.format_b1 = glmmTMB(seconds_log~format + (1|block) + (1|proid), 
                  data = item_block12)

tidy(aov(mod.format_b1))
```

```{r timingmod1, echo = F, fig.cap = "Predictions by condition, using only Block 1 data. Figure A shows log seconds, Figure B shows raw seconds."}
plot_b1 = plot_model(mod.format_b1, type = "pred") 

logplot = plot_b1$format +
  labs(x = NULL,
       y = "Average time\n(log seconds)",
       title = NULL) +
  theme_pubclean()

rawplot = plot_b1$format$data %>% 
  mutate(predicted = exp(predicted),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  mutate(x = factor(x, 
                    labels = c("Adjective\nOnly", 
                               "Am\nAdjective", 
                               "Tend to be\nAdjective", 
                               "Am someone\nwho tends to be\nAdjective"))) %>% 
  ggplot(aes(x = x, y = predicted)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .2) + 
  labs(x = NULL, y = "Average time\n(seconds)", title = NULL) +
  theme_pubclean()

ggarrange(logplot, rawplot, ncol = 1, labels = c("A", "B"))
```


```{r timingdist, echo = F, fig.cap = "Distribution of time by category, block 1 data only"}
means_by_group = item_block12 %>%
  group_by(format) %>% 
  summarise(m = mean(seconds_log),
            s = sd(seconds_log))

item_block12 %>%
  ggplot(aes(x = seconds_log, fill = format)) +
  geom_histogram(bins = 50, color = "white") +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  geom_text(aes(x = 1.5, 
                y = 75, 
                label = paste("M =", round(m,2), 
                              "\nSD =", round(s,2))), 
            data = means_by_group, 
            hjust =0, 
            vjust = 1) +
  facet_wrap(~format) +
  guides(fill = "none") +
  labs(x = "Log-seconds",
    y = "Number of particpants",
       title = "Distribution of log-seconds by format (Block 1 data)") +
  theme_pubr()
```


```{r pairwiseTab, results = 'asis', echo = F}
pairs(emmeans(mod.format_b1, "format"), adjust = "holm") %>% 
  kable(booktabs = T, digits = c(0, 2,2,1,2,3),
        caption = "Pairwise comparisons of timing (log-seconds) across format") %>% 
  kable_styling()
```


### One model for each adjective

We can also repeat this analysis separately for each trait. Results are shown in Table \@ref(tab:itemtable).

```{r, results = 'asis'}
mod_by_item_b1 = item_block12 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lm(seconds_log~format, data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()
```
```{r itemtable, results = 'asis', echo = F}
summary_by_item_b1 = mod_by_item_b1 %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm")) 

summary_by_item_b1 %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>% 
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2,
        booktabs = T, 
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df", "F", "raw", "adj"),
        caption = "Format effects on log-seconds by item (block 1 data only)") %>%
  kable_styling()
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r}
sig_item_b1 = summary_by_item_b1 %>%
  filter(p.value < .05) 

sig_item_b1 = sig_item_b1$item
sig_item_b1
```

Then we create models for each adjective. We use the `emmeans` package to perform pairwise comparisons, again with a Holm correction on the _p_-values. We also plot the means and 95% confidence intervals of each mean. 


### Active

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:activepairs) and means are shown in Figure \@ref(fig:activeplot).


```{r, results = 'asis'}
active_model_b1 = item_block12 %>%
  filter(item == "active") %>%
  lm(seconds_log~format, data = .)

active_em_b1 = emmeans(active_model_b1, "format")
```
```{r activepairs, echo = F, results = 'asis'}
pairs(active_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Active by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r activeplot, echo = F, fig.cap = "Average log-seconds to \"active\" by format (block 1 data only)" }
plot_model(active_model_b1, type = "pred", terms = c("format"))
```


### Adventurous

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:adventurepairs) and means are shown in Figure \@ref(fig:adventureplot).

```{r, results = 'asis'}
adventurous_model_b1 = item_block12 %>%
  filter(item == "adventurous") %>%
  lm(seconds_log~format, data = .)
```
```{r adventurepairs, echo = F, results = 'asis'}
adventurous_em_b1 = emmeans(adventurous_model_b1, "format")
pairs(adventurous_em_b1, adjust = "holm") %>%
   as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Adventurous by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r adventureplot, echo = F, fig.cap = "Average log-seconds to \"adventurous\" by format (block 1 data only)" }
plot_model(adventurous_model_b1, type = "pred", terms = c("format"))
```

### Broadminded

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:broadmindedpairs) and means are shown in Figure \@ref(fig:broadmindedplot).


```{r, results = 'asis'}
broadminded_model_b1 = item_block12 %>%
  filter(item == "broadminded") %>%
  lm(seconds_log~format, data = .)

broadminded_em_b1 = emmeans(broadminded_model_b1, "format")
```
```{r broadmindedpairs, echo = F, results = 'asis'}
pairs(broadminded_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to broadminded by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r broadmindedplot, echo = F, fig.cap = "Average log-seconds to \"broadminded\" by format (block 1 data only)" }
plot_model(broadminded_model_b1, type = "pred", terms = c("format"))
```

### Calm

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:calmpairs) and means are shown in Figure \@ref(fig:calmplot).


```{r, results = 'asis'}
calm_model_b1 = item_block12 %>%
  filter(item == "calm") %>%
  lm(seconds_log~format, data = .)
```
```{r calmpairs, echo = F, results = 'asis'}

calm_em_b1 = emmeans(calm_model_b1, "format")
pairs(calm_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Calm by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r calmplot, echo = F, fig.cap = "Average log-seconds to \"calm\" by format (block 1 data only)" }
plot_model(calm_model_b1, type = "pred", terms = c("format"))
```

### Caring

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:caringpairs) and means are shown in Figure \@ref(fig:caringplot).


```{r, results = 'asis'}
caring_model_b1 = item_block12 %>%
  filter(item == "caring") %>%
  lm(seconds_log~format, data = .)
```
```{r caringpairs, echo = F, results = 'asis'}

caring_em_b1 = emmeans(caring_model_b1, "format")
pairs(caring_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Caring by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r caringplot, echo = F, fig.cap = "Average log-seconds to \"caring\" by format (block 1 data only)" }
plot_model(caring_model_b1, type = "pred", terms = c("format"))
```

### Cautious

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:helpfulpairs) and means are shown in Figure \@ref(fig:helpfulplot).


```{r, results = 'asis'}
cautious_model_b1 = item_block12 %>%
  filter(item == "cautious") %>%
  lm(seconds_log~format, data = .)

cautious_em_b1 = emmeans(cautious_model_b1, "format")
```
```{r cautiouspairs, echo = F, results = 'asis'}
pairs(cautious_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Cautious by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r cautiousplot, echo = F, fig.cap = "Average log-seconds to \"cautious\" by format (block 1 data only)" }
plot_model(cautious_model_b1, type = "pred", terms = c("format"))
```

### Cold

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:coldpairs) and means are shown in Figure \@ref(fig:coldplot).


```{r, results = 'asis'}
cold_model_b1 = item_block12 %>%
  filter(item == "cold") %>%
  lm(seconds_log~format, data = .)

cold_em_b1 = emmeans(cold_model_b1, "format")
```
```{r coldpairs, echo = F, results = 'asis'}
pairs(cold_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Cold by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r coldplot, echo = F, fig.cap = "Average log-seconds to \"cold\" by format (block 1 data only)" }
plot_model(cold_model_b1, type = "pred", terms = c("format"))
```

### Creative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:creativepairs) and means are shown in Figure \@ref(fig:creativeplot).


```{r, results = 'asis'}
creative_model_b1 = item_block12 %>%
  filter(item == "creative") %>%
  lm(seconds_log~format, data = .)

creative_em_b1 = emmeans(creative_model_b1, "format")
```
```{r creativepairs, echo = F, results = 'asis'}
pairs(creative_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Creative by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r creativeplot, echo = F, fig.cap = "Average log-seconds to \"creative\" by format (block 1 data only)" }
plot_model(creative_model_b1, type = "pred", terms = c("format"))
```

### Curious

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:curiouspairs) and means are shown in Figure \@ref(fig:curiousplot).


```{r, results = 'asis'}
curious_model_b1 = item_block12 %>%
  filter(item == "curious") %>%
  lm(seconds_log~format, data = .)

curious_em_b1 = emmeans(curious_model_b1, "format")
```
```{r curiouspairs, echo = F, results = 'asis'}
pairs(curious_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Curious by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r curiousplot, echo = F, fig.cap = "Average log-seconds to \"curious\" by format (block 1 data only)" }
plot_model(curious_model_b1, type = "pred", terms = c("format"))
```

### Friendly

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:friendlypairs) and means are shown in Figure \@ref(fig:friendlyplot).


```{r, results = 'asis'}
friendly_model_b1 = item_block12 %>%
  filter(item == "friendly") %>%
  lm(seconds_log~format, data = .)

friendly_em_b1 = emmeans(friendly_model_b1, "format")
```
```{r friendlypairs, echo = F, results = 'asis'}
pairs(friendly_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Friendly by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r friendlyplot, echo = F, fig.cap = "Average log-seconds to \"friendly\" by format (block 1 data only)" }
plot_model(friendly_model_b1, type = "pred", terms = c("format"))
```

### Hardworking

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:hardworkingpairs) and means are shown in Figure \@ref(fig:hardworkingplot).


```{r, results = 'asis'}
hardworking_model_b1 = item_block12 %>%
  filter(item == "hardworking") %>%
  lm(seconds_log~format, data = .)

hardworking_em_b1 = emmeans(hardworking_model_b1, "format")
```
```{r hardworkingpairs, echo = F, results = 'asis'}
pairs(hardworking_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Hardworking by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r hardworkingplot, echo = F, fig.cap = "Average log-seconds to \"hardworking\" by format (block 1 data only)" }
plot_model(hardworking_model_b1, type = "pred", terms = c("format"))
```

### Helpful

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:helpfulpairs) and means are shown in Figure \@ref(fig:helpfulplot).


```{r, results = 'asis'}
helpful_model_b1 = item_block12 %>%
  filter(item == "helpful") %>%
  lm(seconds_log~format, data = .)

helpful_em_b1 = emmeans(helpful_model_b1, "format")
```
```{r helpfulpairs, echo = F, results = 'asis'}
pairs(helpful_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Helpful by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r helpfulplot, echo = F, fig.cap = "Average log-seconds to \"helpful\" by format (block 1 data only)" }
plot_model(helpful_model_b1, type = "pred", terms = c("format"))
```

### Imaginative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:imaginativepairs) and means are shown in Figure \@ref(fig:imaginativeplot).


```{r, results = 'asis'}
imaginative_model_b1 = item_block12 %>%
  filter(item == "imaginative") %>%
  lm(seconds_log~format, data = .)

imaginative_em_b1 = emmeans(imaginative_model_b1, "format")
```
```{r imaginativepairs, echo = F, results = 'asis'}
pairs(imaginative_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Imaginative by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r imaginativeplot, echo = F, fig.cap = "Average log-seconds to \"imaginative\" by format (block 1 data only)" }
plot_model(imaginative_model_b1, type = "pred", terms = c("format"))
```

### Intelligent

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:intelligentpairs) and means are shown in Figure \@ref(fig:intelligentplot).


```{r, results = 'asis'}
intelligent_model_b1 = item_block12 %>%
  filter(item == "intelligent") %>%
  lm(seconds_log~format, data = .)

intelligent_em_b1 = emmeans(intelligent_model_b1, "format")
```
```{r intelligentpairs, echo = F, results = 'asis'}
pairs(intelligent_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Intelligent by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r intelligentplot, echo = F, fig.cap = "Average log-seconds to \"intelligent\" by format (block 1 data only)" }
plot_model(intelligent_model_b1, type = "pred", terms = c("format"))
```

### Lively

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:livelypairs) and means are shown in Figure \@ref(fig:livelyplot).


```{r, results = 'asis'}
lively_model_b1 = item_block12 %>%
  filter(item == "lively") %>%
  lm(seconds_log~format, data = .)

lively_em_b1 = emmeans(lively_model_b1, "format")
```
```{r livelypairs, echo = F, results = 'asis'}
pairs(lively_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Lively by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r livelyplot, echo = F, fig.cap = "Average log-seconds to \"lively\" by format (block 1 data only)" }
plot_model(lively_model_b1, type = "pred", terms = c("format"))
```

### Organized

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:organizedpairs) and means are shown in Figure \@ref(fig:organizedplot).


```{r, results = 'asis'}
organized_model_b1 = item_block12 %>%
  filter(item == "organized") %>%
  lm(seconds_log~format, data = .)

organized_em_b1 = emmeans(organized_model_b1, "format")
```
```{r organizedpairs, echo = F, results = 'asis'}
pairs(organized_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Organized by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r organizedplot, echo = F, fig.cap = "Average log-seconds to \"organized\" by format (block 1 data only)" }
plot_model(organized_model_b1, type = "pred", terms = c("format"))
```

### Outgoing

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:outgoingpairs) and means are shown in Figure \@ref(fig:outgoingplot).


```{r, results = 'asis'}
outgoing_model_b1 = item_block12 %>%
  filter(item == "outgoing") %>%
  lm(seconds_log~format, data = .)

outgoing_em_b1 = emmeans(outgoing_model_b1, "format")
```
```{r outgoingpairs, echo = F, results = 'asis'}
pairs(outgoing_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Outgoing by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r outgoingplot, echo = F, fig.cap = "Average log-seconds to \"outgoing\" by format (block 1 data only)" }
plot_model(outgoing_model_b1, type = "pred", terms = c("format"))
```

### Quiet

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:quietpairs) and means are shown in Figure \@ref(fig:quietplot).


```{r, results = 'asis'}
quiet_model_b1 = item_block12 %>%
  filter(item == "quiet") %>%
  lm(seconds_log~format, data = .)

quiet_em_b1 = emmeans(quiet_model_b1, "format")
```
```{r quietpairs, echo = F, results = 'asis'}
pairs(quiet_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Quiet by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r quietplot, echo = F, fig.cap = "Average log-seconds to \"quiet\" by format (block 1 data only)" }
plot_model(quiet_model_b1, type = "pred", terms = c("format"))
```

### Relaxed

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:relaxedpairs) and means are shown in Figure \@ref(fig:relaxedplot).


```{r, results = 'asis'}
relaxed_model_b1 = item_block12 %>%
  filter(item == "relaxed") %>%
  lm(seconds_log~format, data = .)

relaxed_em_b1 = emmeans(relaxed_model_b1, "format")
```
```{r relaxedpairs, echo = F, results = 'asis'}
pairs(relaxed_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Relaxed by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r relaxedplot, echo = F, fig.cap = "Average log-seconds to \"relaxed\" by format (block 1 data only)" }
plot_model(relaxed_model_b1, type = "pred", terms = c("format"))
```

### Responsible

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:responsiblepairs) and means are shown in Figure \@ref(fig:responsibleplot).


```{r, results = 'asis'}
responsible_model_b1 = item_block12 %>%
  filter(item == "responsible") %>%
  lm(seconds_log~format, data = .)

responsible_em_b1 = emmeans(responsible_model_b1, "format")
```
```{r responsiblepairs, echo = F, results = 'asis'}
pairs(responsible_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Responsible by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r responsibleplot, echo = F, fig.cap = "Average log-seconds to \"responsible\" by format (block 1 data only)" }
plot_model(responsible_model_b1, type = "pred", terms = c("format"))
```

### Self-disciplined

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:selfdisciplinedpairs) and means are shown in Figure \@ref(fig:selfdisciplinedplot).


```{r, results = 'asis'}
selfdisciplined_model_b1 = item_block12 %>%
  filter(item == "selfdisciplined") %>%
  lm(seconds_log~format, data = .)

selfdisciplined_em_b1 = emmeans(selfdisciplined_model_b1, "format")
```
```{r selfdisciplinedpairs, echo = F, results = 'asis'}
pairs(selfdisciplined_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Self-disciplined by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r selfdisciplinedplot, echo = F, fig.cap = "Average log-seconds to \"selfdisciplined\" by format (block 1 data only)" }
plot_model(selfdisciplined_model_b1, type = "pred", terms = c("format"))
```

### Shy

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:shypairs) and means are shown in Figure \@ref(fig:shyplot).


```{r, results = 'asis'}
shy_model_b1 = item_block12 %>%
  filter(item == "shy") %>%
  lm(seconds_log~format, data = .)

shy_em_b1 = emmeans(shy_model_b1, "format")
```
```{r shypairs, echo = F, results = 'asis'}
pairs(shy_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Shy by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r shyplot, echo = F, fig.cap = "Average log-seconds to \"shy\" by format (block 1 data only)" }
plot_model(shy_model_b1, type = "pred", terms = c("format"))
```

### Soft-hearted

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:softpairs) and means are shown in Figure \@ref(fig:softplot).


```{r, results = 'asis'}
softhearted_model_b1 = item_block12 %>%
  filter(item == "softhearted") %>%
  lm(seconds_log~format, data = .)
```
```{r softpairs, echo = F, results = 'asis'}

softhearted_em_b1 = emmeans(softhearted_model_b1, "format")
pairs(softhearted_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Soft-hearted by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r softplot, echo = F, fig.cap = "Average log-seconds to \"softhearted\" by format (block 1 data only)" }
plot_model(softhearted_model_b1, type = "pred", terms = c("format"))
```

### Sophisticated

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:sophisticatedpairs) and means are shown in Figure \@ref(fig:sophisticatedplot).


```{r, results = 'asis'}
sophisticated_model_b1 = item_block12 %>%
  filter(item == "sophisticated") %>%
  lm(seconds_log~format, data = .)

sophisticated_em_b1 = emmeans(sophisticated_model_b1, "format")
```
```{r sophisticatedpairs, echo = F, results = 'asis'}
pairs(sophisticated_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Sophisticated by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r sophisticatedplot, echo = F, fig.cap = "Average log-seconds to \"sophisticated\" by format (block 1 data only)" }
plot_model(sophisticated_model_b1, type = "pred", terms = c("format"))
```


### Sympathetic

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:symppairs) and means are shown in Figure \@ref(fig:sympplot).


```{r, results = 'asis'}
sympathetic_model_b1 = item_block12 %>%
  filter(item == "sympathetic") %>%
  lm(seconds_log~format, data = .)
```
```{r symppairs, echo = F, results = 'asis'}

sympathetic_em_b1 = emmeans(sympathetic_model_b1, "format")
pairs(sympathetic_em_b1, adjust = "holm") %>%
   as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Sympathetic by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r sympplot, echo = F, fig.cap = "Average log-seconds to \"sympathetic\" by format (block 1 data only)" }
plot_model(sympathetic_model_b1, type = "pred", terms = c("format"))
```

### Talkative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:talkativepairs) and means are shown in Figure \@ref(fig:talkativeplot).


```{r, results = 'asis'}
talkative_model_b1 = item_block12 %>%
  filter(item == "talkative") %>%
  lm(seconds_log~format, data = .)

talkative_em_b1 = emmeans(talkative_model_b1, "format")
```
```{r talkativepairs, echo = F, results = 'asis'}
pairs(talkative_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Talkative by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r talkativeplot, echo = F, fig.cap = "Average log-seconds to \"talkative\" by format (block 1 data only)" }
plot_model(talkative_model_b1, type = "pred", terms = c("format"))
```

### Thorough

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:thoroughpairs) and means are shown in Figure \@ref(fig:thoroughplot).


```{r, results = 'asis'}
thorough_model_b1 = item_block12 %>%
  filter(item == "thorough") %>%
  lm(seconds_log~format, data = .)

thorough_em_b1 = emmeans(thorough_model_b1, "format")
```
```{r thoroughpairs, echo = F, results = 'asis'}
pairs(thorough_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Thorough by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r thoroughplot, echo = F, fig.cap = "Average log-seconds to \"thorough\" by format (block 1 data only)" }
plot_model(thorough_model_b1, type = "pred", terms = c("format"))
```

### Thrifty

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:thriftypairs) and means are shown in Figure \@ref(fig:thriftyplot).


```{r, results = 'asis'}
thrifty_model_b1 = item_block12 %>%
  filter(item == "thrifty") %>%
  lm(seconds_log~format, data = .)

thrifty_em_b1 = emmeans(thrifty_model_b1, "format")
```
```{r thriftypairs, echo = F, results = 'asis'}
pairs(thrifty_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Thrifty by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r thriftyplot, echo = F, fig.cap = "Average log-seconds to \"thrifty\" by format (block 1 data only)" }
plot_model(thrifty_model_b1, type = "pred", terms = c("format"))
```

### Uncreative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:uncreativepairs) and means are shown in Figure \@ref(fig:uncreativeplot).


```{r, results = 'asis'}
uncreative_model_b1 = item_block12 %>%
  filter(item == "uncreative") %>%
  lm(seconds_log~format, data = .)

uncreative_em_b1 = emmeans(uncreative_model_b1, "format")
```
```{r uncreativepairs, echo = F, results = 'asis'}
pairs(uncreative_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Uncreative by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r uncreativeplot, echo = F, fig.cap = "Average log-seconds to \"uncreative\" by format (block 1 data only)" }
plot_model(uncreative_model_b1, type = "pred", terms = c("format"))
```

### Unintellectual

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:unintellectualpairs) and means are shown in Figure \@ref(fig:unintellectualplot).


```{r, results = 'asis'}
unintellectual_model_b1 = item_block12 %>%
  filter(item == "unintellectual") %>%
  lm(seconds_log~format, data = .)

unintellectual_em_b1 = emmeans(unintellectual_model_b1, "format")
```
```{r unintellectualpairs, echo = F, results = 'asis'}
pairs(unintellectual_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Unintellectual by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r unintellectualplot, echo = F, fig.cap = "Average log-seconds to \"unintellectual\" by format (block 1 data only)" }
plot_model(unintellectual_model_b1, type = "pred", terms = c("format"))
```

### Unsympathetic

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:unsympatheticpairs) and means are shown in Figure \@ref(fig:unsympatheticplot).


```{r, results = 'asis'}
unsympathetic_model_b1 = item_block12 %>%
  filter(item == "unsympathetic") %>%
  lm(seconds_log~format, data = .)

unsympathetic_em_b1 = emmeans(unsympathetic_model_b1, "format")
```
```{r unsympatheticpairs, echo = F, results = 'asis'}
pairs(unsympathetic_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Unsympathetic by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r unsympatheticplot, echo = F, fig.cap = "Average log-seconds to \"unsympathetic\" by format (block 1 data only)" }
plot_model(unsympathetic_model_b1, type = "pred", terms = c("format"))
```

### Warm

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:warmpairs) and means are shown in Figure \@ref(fig:warmplot).


```{r, results = 'asis'}
warm_model_b1 = item_block12 %>%
  filter(item == "warm") %>%
  lm(seconds_log~format, data = .)

warm_em_b1 = emmeans(warm_model_b1, "format")
```
```{r warmpairs, echo = F, results = 'asis'}
pairs(warm_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Warm by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r warmplot, echo = F, fig.cap = "Average log-seconds to \"warm\" by format (block 1 data only)" }
plot_model(warm_model_b1, type = "pred", terms = c("format"))
```

### Careless

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:carelesspairs) and means are shown in Figure \@ref(fig:carelessplot).


```{r, results = 'asis'}
careless_model_b1 = item_block12 %>%
  filter(item == "careless") %>%
  lm(seconds_log~format, data = .)

careless_em_b1 = emmeans(careless_model_b1, "format")
```
```{r carelesspairs, echo = F, results = 'asis'}
pairs(careless_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Careless by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r carelessplot, echo = F, fig.cap = "Average log-seconds to \"careless\" by format (block 1 data only)" }
plot_model(careless_model_b1, type = "pred", terms = c("format"))
```

### Impulsive

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:impulsivepairs) and means are shown in Figure \@ref(fig:impulsiveplot).


```{r, results = 'asis'}
impulsive_model_b1 = item_block12 %>%
  filter(item == "impulsive") %>%
  lm(seconds_log~format, data = .)

impulsive_em_b1 = emmeans(impulsive_model_b1, "format")
```
```{r impulsivepairs, echo = F, results = 'asis'}
pairs(impulsive_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Impulsive by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r impulsiveplot, echo = F, fig.cap = "Average log-seconds to \"impulsive\" by format (block 1 data only)" }
plot_model(impulsive_model_b1, type = "pred", terms = c("format"))
```

### Moody

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:moodypairs) and means are shown in Figure \@ref(fig:moodyplot).


```{r, results = 'asis'}
moody_model_b1 = item_block12 %>%
  filter(item == "moody") %>%
  lm(seconds_log~format, data = .)

moody_em_b1 = emmeans(moody_model_b1, "format")
```
```{r moodypairs, echo = F, results = 'asis'}
pairs(moody_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Moody by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r moodyplot, echo = F, fig.cap = "Average log-seconds to \"moody\" by format (block 1 data only)" }
plot_model(moody_model_b1, type = "pred", terms = c("format"))
```

### Nervous

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:nervouspairs) and means are shown in Figure \@ref(fig:nervousplot).


```{r, results = 'asis'}
nervous_model_b1 = item_block12 %>%
  filter(item == "nervous") %>%
  lm(seconds_log~format, data = .)

nervous_em_b1 = emmeans(nervous_model_b1, "format")
```
```{r nervouspairs, echo = F, results = 'asis'}
pairs(nervous_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Nervous by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r nervousplot, echo = F, fig.cap = "Average log-seconds to \"nervous\" by format (block 1 data only)" }
plot_model(nervous_model_b1, type = "pred", terms = c("format"))
```

### Reckless

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:recklesspairs) and means are shown in Figure \@ref(fig:recklessplot).


```{r, results = 'asis'}
reckless_model_b1 = item_block12 %>%
  filter(item == "reckless") %>%
  lm(seconds_log~format, data = .)

reckless_em_b1 = emmeans(reckless_model_b1, "format")
```
```{r recklesspairs, echo = F, results = 'asis'}
pairs(reckless_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Reckless by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r recklessplot, echo = F, fig.cap = "Average log-seconds to \"reckless\" by format (block 1 data only)" }
plot_model(reckless_model_b1, type = "pred", terms = c("format"))
```

### Worrying

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:worryingpairs) and means are shown in Figure \@ref(fig:worryingplot).


```{r, results = 'asis'}
worrying_model_b1 = item_block12 %>%
  filter(item == "worrying") %>%
  lm(seconds_log~format, data = .)

worrying_em_b1 = emmeans(worrying_model_b1, "format")
```
```{r worryingpairs, echo = F, results = 'asis'}
pairs(worrying_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Worrying by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r worryingplot, echo = F, fig.cap = "Average log-seconds to \"worrying\" by format (block 1 data only)" }
plot_model(worrying_model_b1, type = "pred", terms = c("format"))
```

## Inclusion of "I" (Blocks 1 and 3)

We used a multilevel model, nesting response within participant to account for dependence. Our primary predictors are format and also the presence of the word "I". Here, we use data from blocks 1 and 3. Results are depicted in Figure \@ref(fig:secondsi).

```{r}
items_13 = items_df %>% 
  filter(block %in% c("1","3")) %>% 
  filter(condition != "A") %>% 
  filter(time2 == "yes") %>% 
  filter(!is.infinite(seconds_log))
```

```{r}
mod.format_b3_1 = glmmTMB(seconds_log~format + i + (1|proid), 
                  data = items_13)
tidy(aov(mod.format_b3_1)) %>% 
  mutate(p.value = papaja::printp(p.value))

mod.format_b3_2 = glmmTMB(seconds_log~format*i + (1|proid), 
                  data = items_13)
tidy(aov(mod.format_b3_2)) %>% 
  mutate(p.value = papaja::printp(p.value))
```

```{r secondsi, echo = F, fig.cap = "Predicted log-seconds on personality items by condition and I, using Block 1 and Block 3 data."}
plot_b2 = plot_model(mod.format_b3_2, type = "pred", terms = c("format", "i")) 

plot_b2 +
  labs(x = NULL,
       y = "Average log-seconds",
       title = "Average responses by item formatting (Block 1 and Block 3)",
       color = "I") +
  theme_pubclean()
```

### One model for each adjective

Additive effects of I (controlling for format) are summarized in Table \@ref(tab:itemi). Tests of the interaction of I with format (for each item) are summarized in Table \@ref(tab:iinteraction). 

```{r, results = 'asis'}
mod_by_item_i1 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~glmmTMB(seconds_log~format+i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, aov)) %>% 
  ungroup()
```

```{r}
summary_by_item_i1 = mod_by_item_i1 %>% 
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"))
```
```{r itemi, echo = F, results = 'asis'}
summary_by_item_i1 %>%
  arrange(reverse, item) %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2, booktabs = T,
        caption = "Additive effect of I on timing for each item") %>%
  kable_styling()
```


```{r, results = 'asis'}
mod_by_item_i2 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~glmmTMB(seconds_log~format*i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, aov)) %>% 
  ungroup()
```
```{r iinteraction, echo = F, results = 'asis'}
summary_by_item_i2 = mod_by_item_i2 %>% 
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format:i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_i2 %>%
  arrange(reverse, item) %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2, booktabs = T,
        caption = "Interaction of I with format on timing for each item") %>%
  kable_styling()
```

#### Outgoing


Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:outgoingpairsi) and means are shown in Figure \@ref(fig:outgoingplot).


```{r, results = 'asis'}
outgoing_model_b1i = items_13 %>%
  filter(item == "outgoing") %>%
  lm(seconds_log~format*i, data = .)

outgoing_em_b1i = emmeans(outgoing_model_b1i, ~ "format*i")
```
```{r outgoingpairsi, echo = F, results = 'asis'}
pairs(outgoing_em_b1i, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(
    across( starts_with("p"), printp ), # format p-values
    contrast = str_replace(contrast, "Absent", "I-Absent"),
    contrast = str_replace(contrast, "Present", "I-Present")) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Outgoing by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r outgoingploti, echo = F, fig.cap = "Average log-seconds to \"outgoing\" by format (block 1 data only)" }
plot_model(outgoing_model_b1i, type = "pred", terms = c("format", "i"))
```