---
title: "Does item format impact timing?"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    always_allow_html: true
---


```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```


```{r, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(glmmTMB) # for mulitlevel modeling
library(broom) # for tidying
library(marginaleffects) # for comparisons
library(effectsize) # for effect sizes
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tablesgi
library(papaja) # for formatting numbers
```

```{r, echo = F}
load(here("objects/items_df.Rds"))
load(here("objects/reverse_vector.Rds"))
```


## Effect of format on timing (Blocks 1 and 2 data)

We used a multilevel model, nesting log-seconds within participant to account for dependence. Our primary predictor was format. Here, we use only Blocks 1 and 2 as data. Results are depicted in Figure \@ref(fig:timingmod1). The full distribution of timing (in log-seconds) is shown in Figure \@ref(fig:timingdist). Tests of pairwise comparisons are shown in Table \@ref(tab:pairwiseTab).

```{r}
item_block12 = filter(items_df, block %in% c("1", "2")) %>% 
  filter(!is.infinite(seconds_log)) # this was added post pre-registration

mod.format_b1 = glmmTMB(seconds_log~format + (1|block) + (1|proid), 
                  data = item_block12)

tidy(aov(mod.format_b1))
```

```{r}
effectsize::hedges_g(
  seconds_log ~ format, 
  data = filter(item_block12, format %in% c("Adjective\nOnly", "Am\nAdjective"))
)
effectsize::hedges_g(
  seconds_log ~ format, 
  data = filter(item_block12, format %in% c("Adjective\nOnly", "Tend to be\nAdjective")))

effectsize::hedges_g(
  seconds_log ~ format, 
  data = filter(item_block12, format %in% c("Adjective\nOnly", "Am someone\nwho tends to be\nAdjective")))

effectsize::hedges_g(
  seconds_log ~ format, 
  data = filter(item_block12, format %in% c("Am\nAdjective", "Tend to be\nAdjective")))

effectsize::hedges_g(
  seconds_log ~ format, 
  data = filter(item_block12, format %in% c("Am\nAdjective", "Am someone\nwho tends to be\nAdjective")))

effectsize::hedges_g(
  seconds_log ~ format, 
  data = filter(item_block12, format %in% c("Tend to be\nAdjective", "Am someone\nwho tends to be\nAdjective")))

```

```{r timingmod1, echo = F, fig.cap = "Predictions by condition, using only Block 1 data. Figure A shows log seconds, Figure B shows raw seconds."}

plot_b1 = predictions(mod.format_b1, by = "format", type = "response") 

logplot = plot_b1 %>% 
  ggplot(aes(x = format, y = estimate)) +
  geom_point(stat = "identity") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .5) +
  labs(x = NULL, 
       y = "Average time\n(log seconds)") +
  theme_pubclean()

rawplot = plot_b1 %>% 
  mutate(predicted = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  ggplot(aes(x = format, y = predicted)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .2) + 
  labs(x = NULL, y = "Average time\n(seconds)", title = NULL) +
  theme_pubclean()

ggarrange(logplot, rawplot, ncol = 1, labels = c("A", "B"))
```


```{r timingdist, echo = F, fig.cap = "Distribution of time by category, blocks 1 and 2"}
means_by_group = item_block12 %>%
  group_by(format) %>% 
  summarise(m = mean(seconds_log),
            s = sd(seconds_log))

item_block12 %>%
  ggplot(aes(x = seconds_log, fill = format)) +
  geom_histogram(bins = 50, color = "white") +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  geom_text(aes(x = 1.5, 
                y = 75, 
                label = paste("M =", round(m,2), 
                              "\nSD =", round(s,2))), 
            data = means_by_group, 
            hjust =0, 
            vjust = 1) +
  facet_wrap(~format) +
  guides(fill = "none") +
  labs(x = "Log-seconds",
    y = "Number of particpants",
       title = "Distribution of log-seconds by format (Block 1 data)") +
  theme_pubr()
```


```{r pairwiseTab, results = 'asis', echo = F}
format_b1_comp = avg_comparisons(mod.format_b1, 
                variable = list(format = "pairwise")) 
                
format_b1_comp %>% 
  as.data.frame() |> 
  mutate(
    p.value = p.adjust(p.value, method = "holm"),
    p.value = printp(p.value),
    across(where(is.numeric), printnum)
    ) %>%
  select(-term, -s.value) %>% 
  kable(
    booktabs = T, 
    digits = 2, 
    caption = "Pairwise comparisons of timing (log-seconds) across format"
    ) %>% 
  kable_styling()
```


### One model for each adjective

We can also repeat this analysis separately for each trait. Results are shown in Table \@ref(tab:itemtable).

```{r, results = 'asis'}
mod_by_item_b1 = item_block12 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lm(seconds_log~format, data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()
```
```{r itemtable, results = 'asis', echo = F}
summary_by_item_b1 = mod_by_item_b1 %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm")) 

summary_by_item_b1 %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>% 
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2,
        booktabs = T, 
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df", "F", "raw", "adj"),
        caption = "Format effects on log-seconds by item (blocks 1 and 2)") %>%
  kable_styling()
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r}
sig_item_b1 = summary_by_item_b1 %>%
  filter(p.value < .05) 

sig_item_b1 = sig_item_b1$item
sig_item_b1
```

Then we create models for each adjective. We use the `marginaleffects` package to perform pairwise comparisons, again with a Holm correction on the _p_-values. We also plot the means and 95% confidence intervals of each mean. 

```{r}
adjective_timing = function(adjective){
  
  model = item_block12 %>%
    filter(item == adjective) %>%
    lm(seconds_log~format, data = .)
  
  comp = avg_comparisons(model, 
                         variables = list(format = "pairwise")) |> as.data.frame()
  comp$p.value = p.adjust(comp$p.value, method = "holm")
  
  comp = comp %>% 
    mutate(
    across( starts_with("p"), printp )) 
  
  caption = paste("Differences in log-seconds to", 
                  adjective,
                  "by format (blocks 1 and 2)")
  
  
  plot = avg_predictions(model, variables = "format") %>% 
    mutate(across(where(is.numeric), exp)) %>% 
    ggplot(aes(x = format, y = estimate)) +
    geom_point() +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .3) +
    labs(
      x = NULL, 
      y = "seconds", 
      title = paste0("Average response time to ", str_to_sentence(adjective))) +
    theme_pubclean()
  
  return(list(
    comp = comp,
    caption = caption,
    plot = plot
  ))
}
```



### Active

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:activepairs) and means are shown in Figure \@ref(fig:activeplot).


```{r, results = 'asis'}
active_model = adjective_timing("active")
```

```{r activepairs, echo = F, results = 'asis'}
active_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = active_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
  
```

```{r activeplot, echo = F, fig.cap = "Average seconds to respond to \"active\" by format (blocks 1 and 2)." }
active_model$plot
```


### Adventurous

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:adventurouspairs) and means are shown in Figure \@ref(fig:adventurousplot).


```{r, results = 'asis'}
adventurous_model = adjective_timing("adventurous")
```
```{r adventurouspairs, echo = F, results = 'asis'}
adventurous_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = adventurous_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r adventurousplot, echo = F, fig.cap = "Average seconds to respond to \"adventurous\" by format (blocks 1 and 2)" }
adventurous_model$plot
```


### Broadminded

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:broadmindedpairs) and means are shown in Figure \@ref(fig:broadmindedplot).


```{r, results = 'asis'}
broadminded_model = adjective_timing("broadminded")
```
```{r broadmindedpairs, echo = F, results = 'asis'}
broadminded_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = broadminded_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r broadmindedplot, echo = F, fig.cap = "Average log-seconds to \"broadminded\" by format (blocks 1 and 2)" }
broadminded_model$plot
```

### Calm

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:calmpairs) and means are shown in Figure \@ref(fig:calmplot).


```{r, results = 'asis'}
calm_model = adjective_timing("calm")
```
```{r calmpairs, echo = F, results = 'asis'}
calm_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = calm_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r calmplot, echo = F, fig.cap = "Average log-seconds to \"calm\" by format (blocks 1 and 2)" }
calm_model$plot
```

### Caring

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:caringpairs) and means are shown in Figure \@ref(fig:caringplot).


```{r, results = 'asis'}
caring_model = adjective_timing("caring")
```
```{r caringpairs, echo = F, results = 'asis'}
caring_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = caring_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r caringplot, echo = F, fig.cap = "Average log-seconds to \"caring\" by format (blocks 1 and 2)" }
caring_model$plot
```

### Cautious

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:helpfulpairs) and means are shown in Figure \@ref(fig:helpfulplot).


```{r, results = 'asis'}
cautious_model = adjective_timing("cautious")
```
```{r cautiouspairs, echo = F, results = 'asis'}
cautious_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = cautious_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r cautiousplot, echo = F, fig.cap = "Average log-seconds to \"cautious\" by format (blocks 1 and 2)" }
cautious_model$plot
```

### Cold

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:coldpairs) and means are shown in Figure \@ref(fig:coldplot).


```{r, results = 'asis'}
cold_model = adjective_timing("cold")
```
```{r coldpairs, echo = F, results = 'asis'}
cold_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = cold_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r coldplot, echo = F, fig.cap = "Average log-seconds to \"cold\" by format (blocks 1 and 2)" }
cold_model$plot
```

### Creative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:creativepairs) and means are shown in Figure \@ref(fig:creativeplot).


```{r, results = 'asis'}
creative_model = adjective_timing("creative")
```
```{r creativepairs, echo = F, results = 'asis'}
creative_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = creative_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r creativeplot, echo = F, fig.cap = "Average log-seconds to \"creative\" by format (blocks 1 and 2)" }
creative_model$plot
```

### Curious

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:curiouspairs) and means are shown in Figure \@ref(fig:curiousplot).


```{r, results = 'asis'}
curious_model = adjective_timing("curious")
```
```{r curiouspairs, echo = F, results = 'asis'}
curious_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = curious_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r curiousplot, echo = F, fig.cap = "Average log-seconds to \"curious\" by format (blocks 1 and 2)" }
curious_model$plot
```

### Friendly

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:friendlypairs) and means are shown in Figure \@ref(fig:friendlyplot).


```{r, results = 'asis'}
friendly_model = adjective_timing("friendly")
```
```{r friendlypairs, echo = F, results = 'asis'}
friendly_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = friendly_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r friendlyplot, echo = F, fig.cap = "Average log-seconds to \"friendly\" by format (blocks 1 and 2)" }
friendly_model$plot
```

### Hardworking

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:hardworkingpairs) and means are shown in Figure \@ref(fig:hardworkingplot).


```{r, results = 'asis'}
hardworking_model = adjective_timing("hardworking")
```
```{r hardworkingpairs, echo = F, results = 'asis'}
hardworking_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = hardworking_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r hardworkingplot, echo = F, fig.cap = "Average log-seconds to \"hardworking\" by format (blocks 1 and 2)" }
hardworking_model$plot
```

### Helpful

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:helpfulpairs) and means are shown in Figure \@ref(fig:helpfulplot).


```{r, results = 'asis'}
helpful_model = adjective_timing("helpful")
```
```{r helpfulpairs, echo = F, results = 'asis'}
helpful_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = helpful_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r helpfulplot, echo = F, fig.cap = "Average log-seconds to \"helpful\" by format (blocks 1 and 2)" }
helpful_model$plot
```

### Imaginative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:imaginativepairs) and means are shown in Figure \@ref(fig:imaginativeplot).


```{r, results = 'asis'}
imaginative_model = adjective_timing("imaginative")
```
```{r imaginativepairs, echo = F, results = 'asis'}
imaginative_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = imaginative_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r imaginativeplot, echo = F, fig.cap = "Average log-seconds to \"imaginative\" by format (blocks 1 and 2)" }
imaginative_model$plot
```

### Intelligent

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:intelligentpairs) and means are shown in Figure \@ref(fig:intelligentplot).


```{r, results = 'asis'}
intelligent_model = adjective_timing("intelligent")
```
```{r intelligentpairs, echo = F, results = 'asis'}
intelligent_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = intelligent_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r intelligentplot, echo = F, fig.cap = "Average log-seconds to \"intelligent\" by format (blocks 1 and 2)" }
intelligent_model$plot
```

### Lively

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:livelypairs) and means are shown in Figure \@ref(fig:livelyplot).


```{r, results = 'asis'}
lively_model = adjective_timing("lively")
```
```{r livelypairs, echo = F, results = 'asis'}
lively_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = lively_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r livelyplot, echo = F, fig.cap = "Average log-seconds to \"lively\" by format (blocks 1 and 2)" }
lively_model$plot
```

### Organized

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:organizedpairs) and means are shown in Figure \@ref(fig:organizedplot).


```{r, results = 'asis'}
organized_model = adjective_timing("organized")
```
```{r organizedpairs, echo = F, results = 'asis'}
organized_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = organized_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r organizedplot, echo = F, fig.cap = "Average log-seconds to \"organized\" by format (blocks 1 and 2)" }
organized_model$plot
```

### Outgoing

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:outgoingpairs) and means are shown in Figure \@ref(fig:outgoingplot).


```{r, results = 'asis'}
outgoing_model = adjective_timing("outgoing")
```
```{r outgoingpairs, echo = F, results = 'asis'}
outgoing_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = outgoing_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r outgoingplot, echo = F, fig.cap = "Average log-seconds to \"outgoing\" by format (blocks 1 and 2)" }
outgoing_model$plot
```

### Quiet

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:quietpairs) and means are shown in Figure \@ref(fig:quietplot).


```{r, results = 'asis'}
quiet_model = adjective_timing("quiet")
```
```{r quietpairs, echo = F, results = 'asis'}
quiet_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = quiet_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r quietplot, echo = F, fig.cap = "Average log-seconds to \"quiet\" by format (blocks 1 and 2)" }
quiet_model$plot
```

### Relaxed

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:relaxedpairs) and means are shown in Figure \@ref(fig:relaxedplot).


```{r, results = 'asis'}
relaxed_model = adjective_timing("relaxed")
```

```{r relaxedpairs, echo = F, results = 'asis'}
relaxed_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = relaxed_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r relaxedplot, echo = F, fig.cap = "Average log-seconds to \"relaxed\" by format (blocks 1 and 2)" }
relaxed_model$plot
```

### Responsible

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:responsiblepairs) and means are shown in Figure \@ref(fig:responsibleplot).


```{r, results = 'asis'}
responsible_model = adjective_timing("responsible")
```
```{r responsiblepairs, echo = F, results = 'asis'}
responsible_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = responsible_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r responsibleplot, echo = F, fig.cap = "Average log-seconds to \"responsible\" by format (blocks 1 and 2)" }
responsible_model$plot
```

### Self-disciplined

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:selfdisciplinedpairs) and means are shown in Figure \@ref(fig:selfdisciplinedplot).


```{r, results = 'asis'}
selfdisciplined_model = adjective_timing("selfdisciplined")
```
```{r selfdisciplinedpairs, echo = F, results = 'asis'}
selfdisciplined_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = selfdisciplined_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r selfdisciplinedplot, echo = F, fig.cap = "Average log-seconds to \"selfdisciplined\" by format (blocks 1 and 2)" }
selfdisciplined_model$plot
```

### Shy

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:shypairs) and means are shown in Figure \@ref(fig:shyplot).


```{r, results = 'asis'}
shy_model = adjective_timing("shy")
```
```{r shypairs, echo = F, results = 'asis'}
shy_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = shy_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r shyplot, echo = F, fig.cap = "Average log-seconds to \"shy\" by format (blocks 1 and 2)" }
shy_model$plot
```

### Soft-hearted

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:softpairs) and means are shown in Figure \@ref(fig:softplot).


```{r, results = 'asis'}
softhearted_model = adjective_timing("softhearted")
```
```{r softpairs, echo = F, results = 'asis'}
softhearted_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = softhearted_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r softplot, echo = F, fig.cap = "Average log-seconds to \"softhearted\" by format (blocks 1 and 2)" }
softhearted_model$plot
```

### Sophisticated

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:sophisticatedpairs) and means are shown in Figure \@ref(fig:sophisticatedplot).


```{r, results = 'asis'}
sophisticated_model = adjective_timing("sophisticated")
```
```{r sophisticatedpairs, echo = F, results = 'asis'}
sophisticated_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = sophisticated_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r sophisticatedplot, echo = F, fig.cap = "Average log-seconds to \"sophisticated\" by format (blocks 1 and 2)" }
sophisticated_model$plot
```


### Sympathetic

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:symppairs) and means are shown in Figure \@ref(fig:sympplot).


```{r, results = 'asis'}
sympathetic_model = adjective_timing("sympathetic")
```
```{r symppairs, echo = F, results = 'asis'}
sympathetic_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = sympathetic_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r sympplot, echo = F, fig.cap = "Average log-seconds to \"sympathetic\" by format (blocks 1 and 2)" }
sympathetic_model$plot
```

### Talkative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:talkativepairs) and means are shown in Figure \@ref(fig:talkativeplot).


```{r, results = 'asis'}
talkative_model = adjective_timing("talkative")
```
```{r talkativepairs, echo = F, results = 'asis'}
talkative_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = talkative_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r talkativeplot, echo = F, fig.cap = "Average log-seconds to \"talkative\" by format (blocks 1 and 2)" }
talkative_model$plot
```

### Thorough

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:thoroughpairs) and means are shown in Figure \@ref(fig:thoroughplot).


```{r, results = 'asis'}
thorough_model = adjective_timing("thorough")
```
```{r thoroughpairs, echo = F, results = 'asis'}
thorough_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = thorough_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r thoroughplot, echo = F, fig.cap = "Average log-seconds to \"thorough\" by format (blocks 1 and 2)" }
thorough_model$plot
```

### Thrifty

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:thriftypairs) and means are shown in Figure \@ref(fig:thriftyplot).


```{r, results = 'asis'}
thrifty_model = adjective_timing("thrifty")
```
```{r thriftypairs, echo = F, results = 'asis'}
thrifty_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = thrifty_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r thriftyplot, echo = F, fig.cap = "Average log-seconds to \"thrifty\" by format (blocks 1 and 2)" }
thrifty_model$plot
```

### Uncreative

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:uncreativepairs) and means are shown in Figure \@ref(fig:uncreativeplot).


```{r, results = 'asis'}
uncreative_model = adjective_timing("uncreative")
```
```{r uncreativepairs, echo = F, results = 'asis'}
uncreative_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = uncreative_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r uncreativeplot, echo = F, fig.cap = "Average log-seconds to \"uncreative\" by format (blocks 1 and 2)" }
uncreative_model$plot
```

### Unintellectual

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:unintellectualpairs) and means are shown in Figure \@ref(fig:unintellectualplot).


```{r, results = 'asis'}
unintellectual_model = adjective_timing("unintellectual")
```
```{r unintellectualpairs, echo = F, results = 'asis'}
unintellectual_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = unintellectual_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r unintellectualplot, echo = F, fig.cap = "Average log-seconds to \"unintellectual\" by format (blocks 1 and 2)" }
unintellectual_model$plot
```

### Unsympathetic

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:unsympatheticpairs) and means are shown in Figure \@ref(fig:unsympatheticplot).


```{r, results = 'asis'}
unsympathetic_model = adjective_timing("unsympathetic")
```

```{r unsympatheticpairs, echo = F, results = 'asis'}
unsympathetic_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = unsympathetic_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r unsympatheticplot, echo = F, fig.cap = "Average log-seconds to \"unsympathetic\" by format (blocks 1 and 2)" }
unsympathetic_model$plot
```

### Warm

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:warmpairs) and means are shown in Figure \@ref(fig:warmplot).


```{r, results = 'asis'}
warm_model = adjective_timing("warm")
```
```{r warmpairs, echo = F, results = 'asis'}
warm_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = warm_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r warmplot, echo = F, fig.cap = "Average log-seconds to \"warm\" by format (blocks 1 and 2)" }
warm_model$plot
```

### Careless

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:carelesspairs) and means are shown in Figure \@ref(fig:carelessplot).


```{r, results = 'asis'}
careless_model = adjective_timing("careless")
```
```{r carelesspairs, echo = F, results = 'asis'}
careless_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = careless_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r carelessplot, echo = F, fig.cap = "Average log-seconds to \"careless\" by format (blocks 1 and 2)" }
careless_model$plot
```

### Impulsive

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:impulsivepairs) and means are shown in Figure \@ref(fig:impulsiveplot).


```{r, results = 'asis'}
impulsive_model = adjective_timing("impulsive")
```
```{r impulsivepairs, echo = F, results = 'asis'}
impulsive_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = impulsive_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r impulsiveplot, echo = F, fig.cap = "Average log-seconds to \"impulsive\" by format (blocks 1 and 2)" }
impulsive_model$plot
```

### Moody

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:moodypairs) and means are shown in Figure \@ref(fig:moodyplot).


```{r, results = 'asis'}
moody_model = adjective_timing("moody")
```
```{r moodypairs, echo = F, results = 'asis'}
moody_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = moody_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r moodyplot, echo = F, fig.cap = "Average log-seconds to \"moody\" by format (blocks 1 and 2)" }
moody_model$plot
```

### Nervous

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:nervouspairs) and means are shown in Figure \@ref(fig:nervousplot).


```{r, results = 'asis'}
nervous_model = adjective_timing("nervous")
```
```{r nervouspairs, echo = F, results = 'asis'}
nervous_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = nervous_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r nervousplot, echo = F, fig.cap = "Average log-seconds to \"nervous\" by format (blocks 1 and 2)" }
nervous_model$plot
```

### Reckless

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:recklesspairs) and means are shown in Figure \@ref(fig:recklessplot).


```{r, results = 'asis'}
reckless_model = adjective_timing("reckless")

```
```{r recklesspairs, echo = F, results = 'asis'}
reckless_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = reckless_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```

```{r recklessplot, echo = F, fig.cap = "Average log-seconds to \"reckless\" by format (blocks 1 and 2)" }
reckless_model$plot
```

### Worrying

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:worryingpairs) and means are shown in Figure \@ref(fig:worryingplot).


```{r, results = 'asis'}
worrying_model = adjective_timing("worrying")
```
```{r worryingpairs, echo = F, results = 'asis'}
worrying_model$comp %>% # format p-values
  select(-term, -s.value) %>% 
  kable(booktabs = T,
        digits = 2,
        caption = worrying_model$caption,
        col.names = c("Contrast", "Mean Diff", "SE", "z", "p", "low", "high")) %>%
  kable_styling() %>%
  add_header_above(c(" " = 5, "95% CI" = 2))
```
```{r worryingplot, echo = F, fig.cap = "Average log-seconds to \"worrying\" by format (blocks 1 and 2)" }
worrying_model$plot
```

## Inclusion of "I" (Blocks 1 and 3)

We used a multilevel model, nesting response within participant to account for dependence. Our primary predictors are format and also the presence of the word "I". Here, we use data from blocks 1 and 3. Results are depicted in Figure \@ref(fig:secondsi).

```{r}
items_13 = items_df %>%
  filter(block %in% c("1","3")) %>%
  filter(condition != "A") %>%
  filter(time2 == "yes") %>%
  filter(!is.infinite(seconds_log))

items_13$format = relevel(factor(items_13$format), ref = "Am\nAdjective")
```

```{r}
mod.format_b3_1 = glmmTMB(seconds_log~format + i + (1|proid) + (1|block),
                  data = items_13)
tidy(aov(mod.format_b3_1)) %>%
  mutate(p.value = papaja::printp(p.value))

mod.format_b3_2 = glmmTMB(seconds_log~format*i + (1|proid) + (1|block),
                  data = items_13)
tidy(aov(mod.format_b3_2)) %>%
  mutate(p.value = papaja::printp(p.value))
```

```{r}
effectsize::hedges_g(
  seconds_log ~ i,
  data = items_13
)
```

```{r secondsi, echo = F, fig.cap = "Predicted log-seconds on personality items by condition and I, using Block 1 and Block 3 data."}
second_est = avg_predictions(
  mod.format_b3_2, 
  variables = c("format", "i"), 
  ) %>%
  mutate(across(where(is.numeric), exp)) 

second_est %>%
  ggplot(aes(x = format, y = estimate, group = i)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = .3,
                position = position_dodge(.3)) +
  geom_point(aes(color = i),
             position = position_dodge(.3),
             size = 3) +
  labs(x = NULL,
       y = "seconds",
       title = "Average response time by item formatting (Block 1 and Block 3)",
       color = "I") +
  theme_pubclean()
```

Next, we calculate present the average time per condition. 

```{r, results='asis'}
second_est |> 
  select(format, i, estimate, conf.low, conf.high) |> 
  mutate(across(where(is.numeric), printnum)) |> 
  kable(
    bookdown=T,
    caption = "Estimated seconds by format and inclusion of I (blocks 1 and 3)"
  ) |> 
    kable_styling()
```


### One model for each adjective

Additive effects of I (controlling for format) are summarized in Table \@ref(tab:itemi). Tests of the interaction of I with format (for each item) are summarized in Table \@ref(tab:iinteraction).

```{r, results = 'asis'}
mod_by_item_i1 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~glmmTMB(seconds_log~format+i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, aov)) %>%
  ungroup()
```

```{r}
summary_by_item_i1 = mod_by_item_i1 %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>%
  unnest(cols = c(tidy)) %>%
  filter(term == "i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>%
  mutate(p.adj = p.adjust(p.value, method = "holm"))
```
```{r itemi, echo = F, results = 'asis'}
summary_by_item_i1 %>%
  arrange(reverse, item) %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>%
  kable(digits = 2, booktabs = T,
        caption = "Additive effect of I on timing for each item") %>%
  kable_styling()
```

```{r, results = 'asis'}
mod_by_item_i2 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~glmmTMB(seconds_log~format*i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, aov)) %>%
  ungroup()
```
```{r iinteraction, echo = F, results = 'asis'}
summary_by_item_i2 = mod_by_item_i2 %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>%
  unnest(cols = c(tidy)) %>%
  filter(term == "format:i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>%
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_i2 %>%
  arrange(reverse, item) %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>%
  kable(digits = 2, booktabs = T,
        caption = "Interaction of I with format on timing for each item") %>%
  kable_styling()
```

Here we identify the specific items with significant differences.

```{r}
sig_item_b3 = summary_by_item_i2 %>%
  filter(p.value < .05)

sig_item_b3 = sig_item_b3$item
sig_item_b3
```

```{r}
adjective_timing_i = function(adjective){

  model = items_13 %>%
    filter(item == adjective) %>%
    filter(condition != "A") %>%
    glmmTMB(seconds_log~format*i + (1|proid), data = .)

  plot = avg_predictions(model, variables = c("format", "i")) %>%
    mutate(across(where(is.numeric), exp)) %>%
    ggplot(aes(x = format, y = estimate, group = i)) +
    geom_point(aes(color = i),
               position = position_dodge(.3),
               size = 3) +
    geom_errorbar(
      aes(ymin = conf.low, ymax = conf.high),
               position = position_dodge(.3),
      width = .3) +
    labs(
      x = NULL,
      y = "seconds",
      title = paste0("Average response time to ", str_to_sentence(adjective))) +
    theme_pubclean()

  return(plot)
}
```

### Nervous

```{r, fig.cap = "Average seconds to \"nervous\" by format and inclusion of i (blocks 1 and 3)" }
adjective_timing_i("nervous")
```

### Careless

```{r, fig.cap = "Average seconds to \"careless\" by format and inclusion of i (blocks 1 and 3)"}
adjective_timing_i("careless")
```

