---
title: "Does item format impact timing?"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    always_allow_html: true
---


```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```


```{r, echo = F}
library(here) # for working with files
library(tidyverse) # for cleaning
library(janitor) # for variable names
library(glmmTMB) # for mulitlevel modeling
library(broom) # for tidying
library(emmeans) # for comparisons
library(sjPlot) # for figures
library(ggpubr) # for prettier plots
library(kableExtra) # for nicer tablesgi
library(papaja) # for formatting numbers
```

```{r, echo = F}
load(here("objects/items_df.Rds"))
load(here("objects/reverse_vector.Rds"))
```


## Effect of format on timing (Block 1 data)

We used a multilevel model, nesting log-seconds within participant to account for dependence. Our primary predictor was format. Here, we use only Block 1 data. Results are depicted in Figure \@ref(fig:timingmod1). The full distribution of timing (in log-seconds) is shown in Figure \@ref(fig:timingdist). Tests of pairwise comparisons are shown in Table \@ref(tab:pairwiseTab).

```{r}
item_block1 = filter(items_df, block == "1")

mod.format_b1 = glmmTMB(seconds_log~format + (1|proid), 
                  data = item_block1)
tidy(aov(mod.format_b1))
```

```{r timingmod1, echo = F, fig.cap = "Predictions by condition, using only Block 1 data. Figure A shows log seconds, Figure B shows raw seconds."}
plot_b1 = plot_model(mod.format_b1, type = "pred") 

logplot = plot_b1$format +
  labs(x = NULL,
       y = "Average time\n(log seconds)",
       title = NULL) +
  theme_pubclean()

rawplot = plot_b1$format$data %>% 
  mutate(predicted = exp(predicted),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  mutate(x = factor(x, 
                    labels = c("Adjective\nOnly", 
                               "Am\nAdjective", 
                               "Tend to be\nAdjective", 
                               "Am someone\nwho tends to be\nAdjective"))) %>% 
  ggplot(aes(x = x, y = predicted)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .2) + 
  labs(x = NULL, y = "Average time\n(seconds)", title = NULL) +
  theme_pubclean()

ggarrange(logplot, rawplot, ncol = 1, labels = c("A", "B"))
```


```{r timingdist, echo = F, fig.cap = "Distribution of time by category, block 1 data only"}
means_by_group = item_block1 %>%
  group_by(format) %>% 
  summarise(m = mean(seconds_log),
            s = sd(seconds_log))

item_block1 %>%
  ggplot(aes(x = seconds_log, fill = format)) +
  geom_histogram(bins = 50, color = "white") +
  geom_vline(aes(xintercept = m), data = means_by_group) +
  geom_text(aes(x = 1, 
                y = 40, 
                label = paste("M =", round(m,2), 
                              "\nSD =", round(s,2))), 
            data = means_by_group, 
            hjust =0, 
            vjust = 1) +
  facet_wrap(~format) +
  guides(fill = "none") +
  labs(x = "Log-seconds",
    y = "Number of particpants",
       title = "Distribution of log-seconds by format (Block 1 data)") +
  theme_pubr()
```


```{r pairwiseTab, results = 'asis', echo = F}
pairs(emmeans(mod.format_b1, "format"), adjust = "holm") %>% 
  kable(booktabs = T, digits = c(0, 2,2,1,2,3),
        caption = "Pairwise comparisons of timing (log-seconds) across format") %>% 
  kable_styling()
```


### One model for each adjective

We can also repeat this analysis separately for each trait. Results are shown in Table \@ref(tab:itemtable).

```{r, results = 'asis'}
mod_by_item_b1 = item_block1 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~lm(seconds_log~format, data = .))) %>%
  mutate(aov = map(mod, anova)) %>% 
  ungroup()
```
```{r itemtable, results = 'asis', echo = F}
summary_by_item_b1 = mod_by_item_b1 %>%
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm")) 

summary_by_item_b1 %>%
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  arrange(reverse, item) %>% 
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2,
        booktabs = T, 
        col.names = c("Item", "Reverse\nScored?", "SS", "MS", "df", "F", "raw", "adj"),
        caption = "Format effects on log-seconds by item (block 1 data only)") %>%
  kable_styling()
```

### Pairwise t-tests for significant ANOVAs

Here we identify the specific items with significant differences.

```{r}
sig_item_b1 = summary_by_item_b1 %>%
  filter(p.value < .05) 

sig_item_b1 = sig_item_b1$item
sig_item_b1
```

Then we create models for each adjective. We use the `emmeans` package to perform pairwise comparisons, again with a Holm correction on the _p_-values. We also plot the means and 95% confidence intervals of each mean. 

**This code will have to be changed after final data collection. It is not self-adapting!**


### Helpful

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:helpfulpairs) and means are shown in Figure \@ref(fig:helpfulplot).


```{r, results = 'asis'}
helpful_model_b1 = item_block1 %>%
  filter(item == "helpful") %>%
  lm(seconds_log~format, data = .)

helpful_em_b1 = emmeans(helpful_model_b1, "format")
```
```{r helpfulpairs, echo = F, results = 'asis'}
pairs(helpful_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Helpful by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r helpfulplot, echo = F, fig.cap = "Average log-seconds to \"helpful\" by format (block 1 data only)" }
plot_model(helpful_model_b1, type = "pred", terms = c("format"))
```

### Caring

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:caringpairs) and means are shown in Figure \@ref(fig:caringplot).


```{r, results = 'asis'}
caring_model_b1 = item_block1 %>%
  filter(item == "caring") %>%
  lm(seconds_log~format, data = .)
```
```{r caringpairs, echo = F, results = 'asis'}

caring_em_b1 = emmeans(caring_model_b1, "format")
pairs(caring_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Caring by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r caringplot, echo = F, fig.cap = "Average log-seconds to \"caring\" by format (block 1 data only)" }
plot_model(caring_model_b1, type = "pred", terms = c("format"))
```

### Soft-hearted

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:softpairs) and means are shown in Figure \@ref(fig:softplot).


```{r, results = 'asis'}
softhearted_model_b1 = item_block1 %>%
  filter(item == "softhearted") %>%
  lm(seconds_log~format, data = .)
```
```{r softpairs, echo = F, results = 'asis'}

softhearted_em_b1 = emmeans(softhearted_model_b1, "format")
pairs(softhearted_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Soft-hearted by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r softplot, echo = F, fig.cap = "Average log-seconds to \"softhearted\" by format (block 1 data only)" }
plot_model(softhearted_model_b1, type = "pred", terms = c("format"))
```

### Calm

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:calmpairs) and means are shown in Figure \@ref(fig:calmplot).


```{r, results = 'asis'}
calm_model_b1 = item_block1 %>%
  filter(item == "calm") %>%
  lm(seconds_log~format, data = .)
```
```{r calmpairs, echo = F, results = 'asis'}

calm_em_b1 = emmeans(calm_model_b1, "format")
pairs(calm_em_b1, adjust = "holm") %>%
  as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Calm by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r calmplot, echo = F, fig.cap = "Average log-seconds to \"calm\" by format (block 1 data only)" }
plot_model(calm_model_b1, type = "pred", terms = c("format"))
```

### Sympathetic

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:symppairs) and means are shown in Figure \@ref(fig:sympplot).


```{r, results = 'asis'}
sympathetic_model_b1 = item_block1 %>%
  filter(item == "sympathetic") %>%
  lm(seconds_log~format, data = .)
```
```{r symppairs, echo = F, results = 'asis'}

sympathetic_em_b1 = emmeans(sympathetic_model_b1, "format")
pairs(sympathetic_em_b1, adjust = "holm") %>%
   as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Sympathetic by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r sympplot, echo = F, fig.cap = "Average log-seconds to \"sympathetic\" by format (block 1 data only)" }
plot_model(sympathetic_model_b1, type = "pred", terms = c("format"))
```

### Adventurous

Tests of the pairwise comparisons for this item are shown in Table \@ref(tab:adventurepairs) and means are shown in Figure \@ref(fig:adventureplot).

```{r, results = 'asis'}
adventurous_model_b1 = item_block1 %>%
  filter(item == "adventurous") %>%
  lm(seconds_log~format, data = .)
```
```{r adventurepairs, echo = F, results = 'asis'}
adventurous_em_b1 = emmeans(adventurous_model_b1, "format")
pairs(adventurous_em_b1, adjust = "holm") %>%
   as_tibble() %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  kable(booktabs = T,
        digits = 2,
        caption = "Differences in log-seconds to Adventurous by format (Block 1 data only)",
        col.names = c("Contrast", "Difference in means", "SE", "df", "t", "p")) %>%
  kable_styling()
```

```{r adventureplot, echo = F, fig.cap = "Average log-seconds to \"adventurous\" by format (block 1 data only)" }
plot_model(adventurous_model_b1, type = "pred", terms = c("format"))
```


## Inclusion of "I" (Block 1 and Block 3)

We used a multilevel model, nesting response within participant to account for dependence. Our primary predictors are format and also the presence of the word "I". Here, we use data from blocks 1 and 3. Results are depicted in Figure \@ref(fig:secondsi).

```{r}
items_13 = items_df %>% 
  filter(block %in% c("1","3")) %>% 
  filter(condition != "A") %>% 
  filter(time2 == "yes")
```

```{r}
mod.format_b3_1 = glmmTMB(seconds_log~format + i + (1|proid), 
                  data = items_13)
tidy(aov(mod.format_b3_1)) %>% 
  mutate(p.value = papaja::printp(p.value))

mod.format_b3_2 = glmmTMB(seconds_log~format*i + (1|proid), 
                  data = items_13)
tidy(aov(mod.format_b3_2)) %>% 
  mutate(p.value = papaja::printp(p.value))
```

```{r secondsi, echo = F, fig.cap = "Predicted log-seconds on personality items by condition and I, using Block 1 and Block 3 data."}
plot_b2 = plot_model(mod.format_b3_2, type = "pred", terms = c("format", "i")) 

plot_b2 +
  labs(x = NULL,
       y = "Average log-seconds",
       title = "Average responses by item formatting (Block 1 and Block 3)",
       color = "I") +
  theme_pubclean()
```

### One model for each adjective

Additive effects of I (controlling for format) are summarized in Table \@ref(tab:itemi). Tests of the interaction of I with format (for each item) are summarized in Table \@ref(tab:iinteraction). 

```{r, results = 'asis'}
mod_by_item_i1 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~glmmTMB(seconds_log~format+i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, aov)) %>% 
  ungroup()
```

```{r}
summary_by_item_i1 = mod_by_item_i1 %>% 
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"))
```
```{r itemi, echo = F, results = 'asis'}
summary_by_item_i1 %>%
  arrange(reverse, item) %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2, booktabs = T,
        caption = "Additive effect of I on timing for each item") %>%
  kable_styling()
```


```{r, results = 'asis'}
mod_by_item_i2 = items_13 %>%
  group_by(item) %>%
  nest() %>%
  mutate(mod = map(data, ~glmmTMB(seconds_log~format*i + (1|proid), data = .))) %>%
  mutate(aov = map(mod, aov)) %>% 
  ungroup()
```
```{r iinteraction, echo = F, results = 'asis'}
summary_by_item_i2 = mod_by_item_i2 %>% 
  mutate(tidy = map(aov, broom::tidy)) %>%
  select(item, tidy) %>% 
  unnest(cols = c(tidy)) %>%
  filter(term == "format:i") %>%
  mutate(reverse = case_when(
    item %in% reverse ~ "Y",
    TRUE ~ "N"
  )) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"))

summary_by_item_i2 %>%
  arrange(reverse, item) %>% 
  mutate(across( starts_with("p"), printp )) %>% # format p-values
  select(item, reverse, sumsq, meansq, df, statistic, p.value, p.adj) %>% 
  kable(digits = 2, booktabs = T,
        caption = "Interaction of I with format on timing for each item") %>%
  kable_styling()
```