---
title: "Supplemental file"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: TRUE
---

\renewcommand{\thetable}{S\arabic{table}} 
\renewcommand{\thefigure}{S\arabic{figure}} 

\newpage

# Description of file

Analyses -- including data cleaning, descriptive statistics, and power estimates -- for this project were documented using a series of RMarkdown (.Rmd) files. This document aggregates all files, in the order in which they are meant to be run, into a single RMarkdown file and compiles the output into a single PDF. Those interested in reproducing this document should do the following:

* Check that [LaTex](https://www.latex-project.org/get/) has been installed on their machine.
* Create an RStudio project to store the data and scripts included on this OSF page.
* Download the supplementary workspace (scripts and data) as they are organized on the OSF page -- specifically this means including data in a folder called "deidentified data" and scripts in a folder called "scripts." These folders should be saved in the RStudio project directory.
* Check that the file called `renv.lock` is downloaded and located in the RStudio project folder. This contains a snapshot of the packages and their versions used in this project.

## Reproducibility

In an effort to facilitate the reproducibility of our findings, we have used the `renv` package to document the packages and versions used in this study and to allow others to recreate our working environment. We recommend the following steps to set up your environment before attempting to run any of the code on your local machine:

  1. Use R Version 4.2.3. There are [several ways](https://support.posit.co/hc/en-us/articles/200486138-Using-Different-Versions-of-R) to change the version of R active. We found [RSwitch](https://rud.is/rswitch/) to be the easiest method for toggling between versions of R (only available for Mac).
  
  2. Install the `renv` package and then run the function `renv::restore`. This will read the contained `renv.lock` file to identify which packages (and versions) are necessary for this project, download the required package version from CRAN and install it on your machine. 
  
These two steps should ensure that our code reproduces results identical those reported in our manuscript in supplemental files. 

```{r, include = FALSE}
if (!requireNamespace("remotes"))
  install.packages("remotes")
if (!requireNamespace("renv"))
  remotes::install_github("rstudio/renv")
renv::restore()

# Install devtools package if necessary
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")

# Install the stable development versions from GitHub
if (!requireNamespace("papaja")) devtools::install_github("crsh/papaja")


library(here)
```


\newpage

# Cleaning

```{r, child = here("1-cleaning.Rmd")}
```

\newpage

# Descriptives

```{r, child = here("descriptives.Rmd")}
```

\newpage

# Does item format affect response style?

```{r, child = here("response_style.Rmd")}
```

\newpage

# Does the internal consistency and reliability of Big Five traits vary by item wording?

```{r, child = here("internal.Rmd")}
```

\newpage

# Does the test-retest reliability of personality items change as a function of item wording?

```{r, child = here("test_retest.Rmd")}
```

\newpage

# How does format affect timing of responses?

```{r, child = here("timing_format.Rmd")}
```

\newpage

# How does format affect participants' subjective experience?

```{r, child = here("subjective.Rmd")}
```

\newpage

# Power analysis

```{r, child = here("power.Rmd")}
```

\newpage

# R version and packages

```{r, child = here("workspace.Rmd")}
```
