---
title: "Supplemental file"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: TRUE
    lof: yes
    lot: yes
---

\renewcommand{\thetable}{S\arabic{table}} 
\renewcommand{\thefigure}{S\arabic{figure}} 


```{r, include = FALSE}
library(here)
```


\newpage

# Cleaning

```{r, child = here("1-cleaning.Rmd")}
```

\newpage

# Descriptives

```{r, child = here("descriptives.Rmd")}
```

\newpage

# Does item format affect response?

```{r, child = here("analysis_format.Rmd")}
```

\newpage

# Does the internal consistency of Big Five traits vary by item wording?

```{r, child = here("internal.Rmd")}
```

\newpage

# Does the test-retest reliability of personality items change as a function of item wording?

```{r, child = here("test_retest.Rmd")}
```

\newpage

# How does format affect timining of responses?

```{r, child = here("timing_format.Rmd")}
```

\newpage

# Power analysis

```{r, child = here("power.Rmd")}
```

\newpage

# R version and packages

```{r, child = here("workspace.Rmd")}
```
