---
title: "Supplemental file"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: TRUE
---

\renewcommand{\thetable}{S\arabic{table}} 
\renewcommand{\thefigure}{S\arabic{figure}} 

\newpage

## Description of file

Analyses -- including data cleaning, descriptive statistics, and power estimates -- for this project were documented using a series of RMarkdown (.Rmd) files. This document aggregates all files, in the order in which they are meant to be run, into a single RMarkdown file and compiles the output into a single PDF. Those interested in reproducing this document should do the following:

* Check that [LaTex](https://www.latex-project.org/get/) has been installed on their machine.
* Create an RStudio project to store the data and scripts included on this OSF page.
* Download the supplementary workspace (scripts and data) as they are organized on the OSF page -- specifically this means including data in a folder called "deidentified data" and scripts in a folder called "scripts." These folders should be saved in the RStudio project directory.
* Check that the file called `renv.lock` is downloaded and located in the RStudio project folder. This contains a snapshot of the packages and their versions used in this project.

```{r, include = FALSE}
if (!requireNamespace("remotes"))
  install.packages("remotes")
if (!requireNamespace("renv"))
  remotes::install_github("rstudio/renv")
renv::restore()

# Install devtools package if necessary
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")

# Install the stable development versions from GitHub
if (!requireNamespace("papaja")) devtools::install_github("crsh/papaja")


library(here)
```


\newpage

# Cleaning

```{r, child = here("1-cleaning.Rmd")}
```

\newpage

# Descriptives

```{r, child = here("descriptives.Rmd")}
```

\newpage

# Does item format affect response style?

```{r, child = here("response_style.Rmd")}
```

\newpage

# Does the internal consistency of Big Five traits vary by item wording?

```{r, child = here("internal.Rmd")}
```

\newpage

# Does the test-retest reliability of personality items change as a function of item wording?

```{r, child = here("test_retest.Rmd")}
```

\newpage

# How does format affect timining of responses?

```{r, child = here("timing_format.Rmd")}
```

\newpage

# Power analysis

```{r, child = here("power.Rmd")}
```

\newpage

# R version and packages

```{r, child = here("workspace.Rmd")}
```
