---
title: "Supplemental file"
date: "Last updated `r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: TRUE
---

```{r, include = FALSE}
library(here)
```


\newpage

# Cleaning

```{r, child = here("1-cleaning.Rmd")}
```

# Descriptives

\newpage

```{r, child = here("descriptives.Rmd")}
```

\newpage

# Does item format affect response?

```{r, child = here("analysis_format.Rmd")}
```

<!-- \newpage -->

<!-- # How is variance in response attributable to participant, adjective, and format? -->

<!-- ```{r, child = here("analysis_propVariance.Rmd")} -->
<!-- ``` -->
\newpage

# Does the internal consistency of Big Five traits vary by item wording?

```{r, child = here("internal.Rmd")}
```

\newpage

# Does the test-retest reliability of personality items change as a function of item wording?

```{r, child = here("test_retest.Rmd")}
```

\newpage

# How does format affect timining of responses?

```{r, child = here("timing_format.Rmd")}
```

\newpage

# How does device type affect means and timing of responses?

```{r, child = here("device.Rmd")}
```

\newpage

# Power analysis

```{r, child = here("power.Rmd")}
```
